### 2016-04-26 paper/draft.tex
Added latex sources.

\author{Group 40: Arnold, Gurunat, Huang, \& Qu}
\title{Modular Deep Encoder-Decoders}
\date{\today}
\documentclass[12pt]{article}

\input{\string~/tex_templates/core}

% Custom Title

%\def\maketitle{
    %\centering
    %\par\textbf{\LARGE\@title}
    %\par\hfill
    %\par{\@author, \@date}
    %\par\hfill
    %\par\hfill
    %\rule{\textwidth}{3pt}
%}

\def\maketitle{
    \begin{centering}
    \par\rule{\textwidth}{2pt}
    \par\hfill
    \par\textbf{\LARGE\@title}
    \par\hfill
    \par{\textit{\@author}}
    \par\hfill
    \par{\@date}
    \par\rule{\textwidth}{2pt}
    \end{centering}
}

\begin{document}
\thispagestyle{empty}
\maketitle
\hfill
\begin{abstract}
In this short paper we propose an approach to transfer learning using rich
vector embeddings. The suggested technique can be applied to any supervised
task, and it handles multiple sources and changing sources of data without the
need for retraining. To verify our ideas, we apply our ideas to the task of
text-classification.
\end{abstract}

\section{Introduction}\label{introduction}

Our goal is to generate rich vector embeddings from articles to classify
them into predefined categories. Then, we want to extend our model with
an additional source of data: the title of the videos. To handle this
new knowledge source without retraining our previous model, we suggest
to generate a new embedding that will be used to modify the original
one. This combined embedding will then be used for the classification
task.

More formally, we want to jointly learn a set of \emph{encoder}
functions $\{E_i\}_0^N$ mapping samples $x \sim \chi_i$ from a set of
data distributions $\{\chi_i\}_0^N$ to a fixed-sized vector embedding
$V$.

\[ \forall i \in [0; N]: E_i(x): \chi_i \rightarrow V_i \in \Re^M\]

\[V = \sum_i^N V_i\]

The embedding $V$ is then fed into a decoder function $D$ which in the
case of classification learns a mapping from the vector space of $V$ to
the label space $L$.

\[ D(v): \Re^M \rightarrow L \in \Re^D\]

Finally, we want to extend the set of encoders by learning a new encoder
$E_{N+1}$ which handles samples from a different dataset $\chi_{N+1}$,
without retraining our trained decoders and encoders.

\[ E_{N+1}(x): \chi_{N+1} \rightarrow V_{N+1} \in \Re^M\]

Although we could have used any kind of mapping, we chose to use deep
learning algorithms, as they easily learn hierarchical representations
and have been known to highly outperform other statistical techniques on
natural language tasks. Learning embeddings has been previously done by
\href{References}{{[}1{]}}, although our proposed contribution is
slightly different. \href{References}{{[}1{]}} used deep autoencoders to
obtain a better initialization of the parameters of their model. Our
approach instead is much closer in spirit to the work of Sutskever
\href{References}{{[}3{]}} and Vinyals \href{References}{{[}4{]}}. They
both use encoders on a sequence of data to generate a
\emph{thought-vector} which will then be decoded in the desired terget
sequence. In some sense, our proposal adds the transfer learning
component to their contribution. This approach is also similar to the
work of Karpathy \& al \href{References}{{[}5{]}} where they mapped
images to their captions with embeddings.

\section{Method}\label{method}

\subsection{Materials}\label{materials}

We used the freely available dataset from
\url{https://github.com/ParallelMazen/SaudiNewsNet} The dataset contains
a total of 31,030 Arabic newspaper articles, with title, author, date,
url and content in each entry. Article objects are reprensented in json
format, with UTF-8 encoding. We wrote a script to download the data from
github repo, unzip each file, and read them in as json objects. The
function can also give out content by key values such as title, author
and etc.

\subsection{Procedure}\label{procedure}

The procedure is quite straight-forward. While part of the team worked
on building our tailored dataset, the other half worked on the model
definition and training procedure.

Once every pre-requisite is available, we trained the first encoder
$E_1$ (implemented as a recurrent neural network) to build the embedding
$V_1$. Since we only dealt with a relatively simple classification task,
our decoder $D_1$ was simply a fully connected multi-layer perceptron.
They were jointly trained end-to-end by propagating the gradients
through the embedding from $D_1$ to $E_1$.

The second training step was to train the second encoder $E_2$. Again,
we also performed training end-to-end, but specifically did not
propagate the gradients through $E_1$.

\subsection{Evaluation}\label{evaluation}

\section{Results}\label{results}

\section{Discussion}\label{discussion}

\section{References}\label{references}

Part of the relevant literature review. More literature was involved for
the deep learning part.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Supervised Representation Learning: Transfer Learning with Deep
  Autoencoders, Zhuang \& al,
  http://ijcai.org/Proceedings/15/Papers/578.pdf
\item
  Transfer Learning via Dimensionality Reduction, Pan \& al,

  https://www.cse.ust.hk/\textasciitilde{}jamesk/papers/aaai08.pdf
\item
  Sequence to Sequence Learning with Neural Networks, Sutskever \& al,

  http://arxiv.org/abs/1409.3215
\item
  Grammar as a Foreign Language, Vinyals \& al,
  http://arxiv.org/abs/1412.7449
\item
  Deep Fragment Embeddings for Bidirectional Image Sentence Mapping,
  Karpathy \& al, https://cs.stanford.edu/people/karpathy/nips2014.pdf
\end{enumerate}

%\end{multicols}
\end{document}

### 2016-04-26 paper/proposal.tex
Added latex sources.

--- 2016-04-26 paper/draft.tex
@@
 
-We used the freely available dataset from
-\url{https://github.com/ParallelMazen/SaudiNewsNet} The dataset contains
-a total of 31,030 Arabic newspaper articles, with title, author, date,
-url and content in each entry. Article objects are reprensented in json
-format, with UTF-8 encoding. We wrote a script to download the data from
-github repo, unzip each file, and read them in as json objects. The
-function can also give out content by key values such as title, author
-and etc.
+We will use the freely avaiable dataset from
+\url{https://github.com/ParallelMazen/SaudiNewsNet} and extract the
+titles and articles content. Since the dataset initial purpose is not
+the classification, we will have to slightly rework it to fit our
+purpose.
+
+We will use the neon python library for training deep networks. In the
+case where the training phase would become too expensive, we will also
+rely on the mpi4py library.
 
@@
 
-The procedure is quite straight-forward. While part of the team worked
-on building our tailored dataset, the other half worked on the model
-definition and training procedure.
+The procedure is quite straight-forward. While part of the team will
+work on building our tailored dataset, the other half will work on the
+model definition and training procedure. Coordination at the beginning
+of the work will be curcial. In particular, we plan on feeding the text
+data as a sequence of one-hot character encodings.
 
-Once every pre-requisite is available, we trained the first encoder
+Once every pre-requisite is available, we will train the first encoder
 $E_1$ (implemented as a recurrent neural network) to build the embedding
-$V_1$. Since we only dealt with a relatively simple classification task,
-our decoder $D_1$ was simply a fully connected multi-layer perceptron.
-They were jointly trained end-to-end by propagating the gradients
-through the embedding from $D_1$ to $E_1$.
+$V_1$. Since we will only be dealing with a relatively simple
+classification task, our decoder $D_1$ will simply be a fully connected
+multi-layer perceptron. They will be jointly trained end-to-end by
+propagating the gradients through the embedding from $D_1$ to $E_1$.
 
-The second training step was to train the second encoder $E_2$. Again,
-we also performed training end-to-end, but specifically did not
-propagate the gradients through $E_1$.
+The second training step will be to train the second encoder $E_2$.
+Again, we also perform training end-to-end, but specifically do not
+propagate the gradients through $E_1$. We hope to avoid optimizing the
+parameters of $D_1$, but this might not be practically doable.
 
@@
 
-\section{Results}\label{results}
+The final evaluation scheme is mostly to be determined depending on our
+obtained outcomes. Obviously, we want to compare the new model with the
+the the jointly trained one, as well as a classification baseline.
 
-\section{Discussion}\label{discussion}
+\section{Participants \& Labor
+Division}\label{participants-labor-division}
+
+The participants in alphabetical order:
+
+\begin{itemize}
+\itemsep1pt\parskip0pt\parsep0pt
+\item
+  Seb Arnold - 9013085897 - arnolds@usc.edu
+\item
+  Prashanth Gurunath Shivakumar - 2251924199 - pgurunat@usc.edu
+\item
+  Qiangui Huang - 9532576000 - qianguih@usc.edu
+\item
+  Cheng Qu - 2385279985 - chengqu@usc.edu
+\end{itemize}
+
+Instead of having a fixed division of the labor, we assigned one
+responsible to each task. The responsible acts as a project lead on the
+designed task and other team members can contrbibute to the task as
+required.
+
+\begin{itemize}
+\item
+  Dataset: Cheng
+\item
+  Model Training: Quiangui
+\item
+  Knowledge Transfer: Seb
+\item
+  Report Writing: Prashanth
+\end{itemize}
 

### 2016-04-26 experiment/data.py
Wrapped SaudiNet loader.

@@ -3,17 +3,70 @@
 File responsible for downloading the data and setting up the single and
 multi-data stream.
 """
-import sys, os, json, codecs, urllib, zipfile
+import sys
+import os
+import json
+import codecs
+import urllib
+import zipfile
 import h5py
 from collections import defaultdict
 import regex
 import numpy as np
 import cPickle
+from neon.data.text_preprocessing import get_paddedXY
+from neon.data import ArrayIterator
+from neon.data.dataloaders import load_imdb
+from neon.data.text_preprocessing import pad_data
+
+VOCAB_SIZE = 20000
+SENTENCE_LENGTH = 128
+
+
+def get_saudinet_data(args):
+    """ Returns a train and validation dataset from SaudiNewsNet. """
+    # get the preprocessed and tokenized data
+    article = load_articles("./SaudiNewsNet")
+    fname_h5, fname_vocab = preprocess_data_train(article, 'content', './experiments/labeledTrainData.tsv')
+
+    h5f = h5py.File(fname_h5, 'r')
+    data, h5train, h5valid = h5f['data'], h5f['train'], h5f['valid']
+    ntrain, nvalid, nclass, vocab_size = data.attrs[
+        'ntrain'], data.attrs['nvalid'], data.attrs['nclass'], data.attrs['vocab_size']
+
+    # make train dataset
+    Xy = h5train[:ntrain]
+    X = [xy[1:] for xy in Xy]
+    y = [xy[0] for xy in Xy]
+    X_train, y_train = get_paddedXY(X, y, vocab_size=vocab_size, sentence_length=SENTENCE_LENGTH)
+    train_set = ArrayIterator(X_train, y_train, nclass=nclass)
+
+    # make valid dataset
+    Xy = h5valid[:nvalid]
+    X = [xy[1:] for xy in Xy]
+    y = [xy[0] for xy in Xy]
+    X_valid, y_valid = get_paddedXY(
+        X, y, vocab_size=vocab_size, sentence_length=SENTENCE_LENGTH)
+    valid_set = ArrayIterator(X_valid, y_valid, nclass=nclass)
+
+    return train_set, valid_set, nclass
+
+
+def get_imdb(args):
+    """DUmmy dataset for dev."""
+    path = load_imdb(path=args.data_dir)
+    (X_train, y_train), (X_test, y_test), nclass = pad_data(
+        path, vocab_size=VOCAB_SIZE, sentence_length=SENTENCE_LENGTH)
[…]

### 2016-04-26 experiment/networks.py

@@ -47,9 +47,8 @@ def get_core_net(embedding_size=128, nout=10):
     glorot = GlorotUniform()
 
     enc = [
-        LookupTable(vocab_size=VOCAB_SIZE, embedding_dim=128, init=uni),
-        LSTM(embedding_size, glorot, activation=Tanh(),
-             gate_activation=Logistic(), reset_cells=True),
+        LookupTable(vocab_size=VOCAB_SIZE, embedding_dim=embedding_dim, init=uni, pad_idx=0, update=True),
+        LSTM(embedding_size, glorot, activation=Tanh(), gate_activation=Logistic(), reset_cells=True),
         RecurrentSum(),
     ]
 

### 2016-04-26 experiment/train.py

@@ -14,18 +14,7 @@
 # limitations under the License.
 # ----------------------------------------------------------------------------
 """
-  Example that trains LSTM network for sentiment analysis
-  $ python examples/imdb/train.py -e 2 -eval 1 -s imdb.p --vocab_file imdb.vocab
-
-  Get the data from Kaggle:
-
-  https://www.kaggle.com/c/word2vec-nlp-tutorial/data
-
-  If choose to initialize the word embedding layer using Word2Vec, please make sure
-  to get the data GoogleNews-vectors-negative300.bin from:
-
-  https://drive.google.com/file/d/0B7XkCwpI5KDYNlNUTTlSS21pQmM/edit?usp=sharing
-
+    Proof of Concept script to load the data in neon format.
 """
 #from prepare import build_data_train
 from neon.backends import gen_backend
@@ -40,7 +29,7 @@ from neon.callbacks.callbacks import Callbacks
 from neon.data.text_preprocessing import get_paddedXY, get_google_word2vec_W
 import h5py
 import cPickle
-from data import load_articles, preprocess_data_train
+from data import load_articles, preprocess_data_train, get_saudinet_data
 
 # parse the command line arguments
 parser = NeonArgparser(__doc__)
@@ -74,7 +63,7 @@ be = gen_backend(**extract_valid_args(args, gen_backend))
 
 # get the preprocessed and tokenized data
 article = load_articles("../SaudiNewsNet")
-fname_h5, fname_vocab = preprocess_data_train(article, 'content')
+fname_h5, fname_vocab = preprocess_data_train(article, 'content', 'labeledTrainData.tsv')
 
 
 # play around with google-news word vectors for init
@@ -101,17 +90,17 @@ ntrain, nvalid, nclass, vocab_size = data.attrs[
 Xy = h5train[:ntrain]
 X = [xy[1:] for xy in Xy]
 y = [xy[0] for xy in Xy]
-X_train, y_train = get_paddedXY(
-    X, y, vocab_size=vocab_size, sentence_length=sentence_length)
+X_train, y_train = get_paddedXY(X, y, vocab_size=vocab_size, sentence_length=sentence_length)
 train_set = ArrayIterator(X_train, y_train, nclass=nclass)
 
 # make valid dataset
 Xy = h5valid[:nvalid]
 X = [xy[1:] for xy in Xy]
 y = [xy[0] for xy in Xy]
[…]

### 2016-04-26 experiment/train_core.py

@@ -13,14 +13,14 @@ from neon.layers.container import Sequential
 from neon.util.argparser import NeonArgparser, extract_valid_args
 
 from networks import get_core_net, save_core
-from data import get_imdb
+from data import get_imdb, get_saudinet_data
 
 # parse the command line arguments
 parser = NeonArgparser(__doc__)
 args = parser.parse_args(gen_be=False)
 
 # hyperparameters from the reference
-args.batch_size = 128
+# args.batch_size = 32
 args.backend = 'gpu'
 
 
@@ -30,10 +30,11 @@ if __name__ == '__main__':
 
     # Load the dataset
     # TODO: Change IMDB with Arabic articles
-    train_set, test_set = get_imdb(args)
+    # train_set, test_set, nout = get_imdb(args)
+    train_set, test_set, nout = get_saudinet_data(args)
 
     # Build the network
-    (encoder, decoder), cost, opt = get_core_net(nout=2)
+    (encoder, decoder), cost, opt = get_core_net(nout=nout)
     model = Model(layers=Sequential([encoder, decoder, ]))
 
     callbacks = Callbacks(model, eval_set=test_set, **args.callback_args)

### 2016-04-27 experiment/data.py
Made training core working

@@ -19,15 +19,14 @@ from neon.data import ArrayIterator
 from neon.data.dataloaders import load_imdb
 from neon.data.text_preprocessing import pad_data
 
-VOCAB_SIZE = 20000
 SENTENCE_LENGTH = 128
 
 
-def get_saudinet_data(args):
+def get_saudinet_data(args, modality='content'):
     """ Returns a train and validation dataset from SaudiNewsNet. """
     # get the preprocessed and tokenized data
     article = load_articles("./SaudiNewsNet")
-    fname_h5, fname_vocab = preprocess_data_train(article, 'content', './experiments/labeledTrainData.tsv')
+    fname_h5, fname_vocab = preprocess_data_train(article, 'content', './labeledTrainData.tsv')
 
     h5f = h5py.File(fname_h5, 'r')
     data, h5train, h5valid = h5f['data'], h5f['train'], h5f['valid']
@@ -45,11 +44,10 @@ def get_saudinet_data(args):
     Xy = h5valid[:nvalid]
     X = [xy[1:] for xy in Xy]
     y = [xy[0] for xy in Xy]
-    X_valid, y_valid = get_paddedXY(
-        X, y, vocab_size=vocab_size, sentence_length=SENTENCE_LENGTH)
+    X_valid, y_valid = get_paddedXY(X, y, vocab_size=vocab_size, sentence_length=SENTENCE_LENGTH)
     valid_set = ArrayIterator(X_valid, y_valid, nclass=nclass)
 
-    return train_set, valid_set, nclass
+    return train_set, valid_set, nclass, vocab_size
 
 
 def get_imdb(args):
@@ -59,7 +57,7 @@ def get_imdb(args):
         path, vocab_size=VOCAB_SIZE, sentence_length=SENTENCE_LENGTH)
     train_set = ArrayIterator(X_train, y_train, nclass=2)
     test_set = ArrayIterator(X_test, y_test, nclass=2)
-    return (train_set, test_set, 2)
+    return (train_set, test_set, 2, 20000)
 
 
 """

### 2016-04-27 experiment/networks.py

@@ -5,7 +5,6 @@ Defines the network architecture, hyper-params, optimizer and cost to be used
 in the experiements.
 """
 
-from data import VOCAB_SIZE
 from neon.models import Model
 from neon.initializers import GlorotUniform, Uniform
 from neon.optimizers import Adagrad
@@ -35,7 +34,7 @@ def get_cost_opt():
     return cost, opt
 
 
-def get_core_net(embedding_size=128, nout=10):
+def get_core_net(embedding_size=128, vocab_size=20000, nout=10):
     """
     Returns a tuple containing the original encoder and decoder networks.
     embedd_size: size of the output of the encoder
@@ -47,7 +46,7 @@ def get_core_net(embedding_size=128, nout=10):
     glorot = GlorotUniform()
 
     enc = [
-        LookupTable(vocab_size=VOCAB_SIZE, embedding_dim=embedding_dim, init=uni, pad_idx=0, update=True),
+        LookupTable(vocab_size=vocab_size, embedding_dim=embedding_dim, init=uni, pad_idx=0, update=True),
         LSTM(embedding_size, glorot, activation=Tanh(), gate_activation=Logistic(), reset_cells=True),
         RecurrentSum(),
     ]

### 2016-04-27 experiment/train.py

@@ -29,7 +29,7 @@ from neon.callbacks.callbacks import Callbacks
 from neon.data.text_preprocessing import get_paddedXY, get_google_word2vec_W
 import h5py
 import cPickle
-from data import load_articles, preprocess_data_train, get_saudinet_data
+from data import load_articles, preprocess_data_train, get_saudinet_data, get_imdb
 
 # parse the command line arguments
 parser = NeonArgparser(__doc__)
@@ -82,30 +82,29 @@ else:
 
 h5f = h5py.File(fname_h5, 'r')
 data, h5train, h5valid = h5f['data'], h5f['train'], h5f['valid']
-ntrain, nvalid, nclass, vocab_size = data.attrs[
-    'ntrain'], data.attrs['nvalid'], data.attrs['nclass'], data.attrs['vocab_size']
+ntrain, nvalid, nclass, vocab_size = data.attrs['ntrain'], data.attrs['nvalid'], data.attrs['nclass'], data.attrs['vocab_size']
 
 
-# make train dataset
-Xy = h5train[:ntrain]
-X = [xy[1:] for xy in Xy]
-y = [xy[0] for xy in Xy]
-X_train, y_train = get_paddedXY(X, y, vocab_size=vocab_size, sentence_length=sentence_length)
-train_set = ArrayIterator(X_train, y_train, nclass=nclass)
+# # make train dataset
+# Xy = h5train[:ntrain]
+# X = [xy[1:] for xy in Xy]
+# y = [xy[0] for xy in Xy]
+# X_train, y_train = get_paddedXY(X, y, vocab_size=vocab_size, sentence_length=sentence_length)
+# train_set = ArrayIterator(X_train, y_train, nclass=nclass)
 
-# make valid dataset
-Xy = h5valid[:nvalid]
-X = [xy[1:] for xy in Xy]
-y = [xy[0] for xy in Xy]
-X_valid, y_valid = get_paddedXY(X, y, vocab_size=vocab_size, sentence_length=sentence_length)
-valid_set = ArrayIterator(X_valid, y_valid, nclass=nclass)
+# # make valid dataset
+# Xy = h5valid[:nvalid]
+# X = [xy[1:] for xy in Xy]
+# y = [xy[0] for xy in Xy]
+# X_valid, y_valid = get_paddedXY(X, y, vocab_size=vocab_size, sentence_length=sentence_length)
+# valid_set = ArrayIterator(X_valid, y_valid, nclass=nclass)
 
[…]

### 2016-04-27 experiment/train_core.py

@@ -20,7 +20,7 @@ parser = NeonArgparser(__doc__)
 args = parser.parse_args(gen_be=False)
 
 # hyperparameters from the reference
-# args.batch_size = 32
+args.batch_size = 32
 args.backend = 'gpu'
 
 
@@ -29,12 +29,12 @@ if __name__ == '__main__':
     be = gen_backend(**extract_valid_args(args, gen_backend))
 
     # Load the dataset
-    # TODO: Change IMDB with Arabic articles
     # train_set, test_set, nout = get_imdb(args)
-    train_set, test_set, nout = get_saudinet_data(args)
+    train_set, test_set, nout, vocab_size = get_saudinet_data(args)
 
     # Build the network
-    (encoder, decoder), cost, opt = get_core_net(nout=nout)
+    (encoder, decoder), cost, opt = get_core_net(nout=nout, vocab_size=vocab_size)
+    # model = Model(layers=encoder)
     model = Model(layers=Sequential([encoder, decoder, ]))
 
     callbacks = Callbacks(model, eval_set=test_set, **args.callback_args)

### 2016-04-27 experiment/train_augmented.py
Readme update

@@ -14,7 +14,7 @@ from neon.transforms import Accuracy
 from neon.util.argparser import NeonArgparser, extract_valid_args
 
 from networks import load_core, get_title_augmentor
-from data import get_imdb
+from data import get_imdb, get_saudinet_data
 
 # parse the command line arguments
 parser = NeonArgparser(__doc__)
@@ -30,8 +30,8 @@ if __name__ == '__main__':
     be = gen_backend(**extract_valid_args(args, gen_backend))
 
     # Load the dataset
-    # TODO: Change IMDB with Arabic articles
-    train_set, test_set = get_imdb(args)
+    train_content, test_content = get_saudinet_data(args, modality='content')
+    train_title, test_title = get_saudinet_data(args, modality='title')
 
     # Build the network
     encoder, decoder = load_core()

### 2016-04-27 experiment/data.py
Training of multimodal model works.

@@ -26,7 +26,7 @@ def get_saudinet_data(args, modality='content'):
     """ Returns a train and validation dataset from SaudiNewsNet. """
     # get the preprocessed and tokenized data
     article = load_articles("./SaudiNewsNet")
-    fname_h5, fname_vocab = preprocess_data_train(article, 'content', './labeledTrainData.tsv')
+    fname_h5, fname_vocab = preprocess_data_train(article, modality, './labeledTrainData.tsv')
 
     h5f = h5py.File(fname_h5, 'r')
     data, h5train, h5valid = h5f['data'], h5f['train'], h5f['valid']
@@ -38,16 +38,16 @@ def get_saudinet_data(args, modality='content'):
     X = [xy[1:] for xy in Xy]
     y = [xy[0] for xy in Xy]
     X_train, y_train = get_paddedXY(X, y, vocab_size=vocab_size, sentence_length=SENTENCE_LENGTH)
-    train_set = ArrayIterator(X_train, y_train, nclass=nclass)
+    # train_set = ArrayIterator(X_train, y_train, nclass=nclass)
 
     # make valid dataset
     Xy = h5valid[:nvalid]
     X = [xy[1:] for xy in Xy]
     y = [xy[0] for xy in Xy]
     X_valid, y_valid = get_paddedXY(X, y, vocab_size=vocab_size, sentence_length=SENTENCE_LENGTH)
-    valid_set = ArrayIterator(X_valid, y_valid, nclass=nclass)
+    # valid_set = ArrayIterator(X_valid, y_valid, nclass=nclass)
 
-    return train_set, valid_set, nclass, vocab_size
+    return (X_train, y_train), (X_valid, y_valid), nclass, vocab_size
 
 
 def get_imdb(args):

### 2016-04-27 experiment/networks.py

@@ -10,6 +10,7 @@ from neon.initializers import GlorotUniform, Uniform
 from neon.optimizers import Adagrad
 from neon.layers import (
     LSTM,
+    Linear,
     Affine,
     LookupTable,
     RecurrentSum,
@@ -52,7 +53,7 @@ def get_core_net(embedding_size=128, vocab_size=20000, nout=10):
     ]
 
     dec = [
-        Dropout(keep=0.5),
+        Dropout(keep=0.7),
         Affine(nout, glorot, bias=glorot, activation=Softmax())
     ]
 
@@ -60,10 +61,11 @@ def get_core_net(embedding_size=128, vocab_size=20000, nout=10):
     return (enc, dec), cost, opt
 
 
-def load_core():
+def load_core(embedding_size=128):
+    uni = Uniform(low=-0.1/embedding_size, high=0.1/embedding_size)
     enc = Model(SAVE_PATH + 'encoder.neon').layers.layers
     dec = Model(SAVE_PATH + 'decoder.neon').layers.layers
-    return enc, dec
+    return enc, [Linear(embedding_size, uni), ] + dec
 
 
 def save_core(encoder, decoder):
@@ -71,7 +73,7 @@ def save_core(encoder, decoder):
     Model(decoder).save_params(SAVE_PATH + 'decoder.neon', True)
 
 
-def get_title_augmentor(embedding_size=128, path=None):
+def get_title_augmentor(vocab_size=20000, embedding_size=128, path=None):
     """
     Returns the network that will be used to augment the network, to handle
     titles.
@@ -83,7 +85,7 @@ def get_title_augmentor(embedding_size=128, path=None):
     glorot = GlorotUniform()
 
     aug = [
-        LookupTable(vocab_size=VOCAB_SIZE, embedding_dim=128, init=uni),
+        LookupTable(vocab_size=vocab_size, embedding_dim=128, init=uni),
         LSTM(embedding_size, glorot, activation=Tanh(),
              gate_activation=Logistic(), reset_cells=True),
         RecurrentSum(),

### 2016-04-27 experiment/train_augmented.py

@@ -7,11 +7,14 @@ encoder from a different datasource.
 
 
 from neon.backends import gen_backend
+from neon.backends.backend import Block
+from neon.data import ArrayIterator
 from neon.models import Model
 from neon.layers.container import Sequential, MergeMultistream, MergeBroadcast
 from neon.callbacks.callbacks import Callbacks
 from neon.transforms import Accuracy
 from neon.util.argparser import NeonArgparser, extract_valid_args
+from neon.layers import RecurrentSum
 
 from networks import load_core, get_title_augmentor
 from data import get_imdb, get_saudinet_data
@@ -25,27 +28,52 @@ args.batch_size = 128
 args.backend = 'gpu'
 
 
+class MultiModalModel(Model):
+
+    def _epoch_fit(self, dataset, callbacks):
+        epoch = self.epoch_index
+        self.total_cost[:] = 0
+        for mb_idx, (x, t) in enumerate(dataset):
+            callbacks.on_minibatch_begin(epoch, mb_idx)
+            self.be.begin(Block.minibatch, mb_idx)
+            x = self.fprop(x)
+            self.total_cost[:] = self.total_cost + self.cost.get_cost(x, t)
+
+            # deltas back propagate through layers
+            # for every layer in reverse except the 0th one
+            delta = self.cost.get_errors(x, t)
+
+            self.bprop(delta)
+            self.optimizer.optimize(self.layers_to_optimize, epoch=epoch)
+            self.be.end(Block.minibatch, mb_idx)
+            callbacks.on_minibatch_end(epoch, mb_idx)
+        self.total_cost[:] = self.total_cost / dataset.nbatches
+
+
 if __name__ == '__main__':
     # Setup backend
     be = gen_backend(**extract_valid_args(args, gen_backend))
 
     # Load the dataset
-    train_content, test_content = get_saudinet_data(args, modality='content')
-    train_title, test_title = get_saudinet_data(args, modality='title')
+    (X_train_content, y_train_content), (X_test_content, y_test_content), nout, vocab_size = get_saudinet_data(args, modality='content')
+    (X_train_title, y_train_title), (X_test_title, y_test_title), nout, vocab_size = get_saudinet_data(args, modality='title')
+    train_set = ArrayIterator([X_train_content, X_train_title], y_train_content, nout)
+    test_set = ArrayIterator([X_test_content, X_test_title], y_train_content, nout)
 
     # Build the network
[…]

### 2016-04-27 experiment/train_core.py

@@ -6,6 +6,7 @@ the decoder.
 """
 
 from neon.backends import gen_backend
+from neon.data import ArrayIterator
 from neon.models import Model
 from neon.callbacks.callbacks import Callbacks
 from neon.transforms import Accuracy
@@ -20,7 +21,7 @@ parser = NeonArgparser(__doc__)
 args = parser.parse_args(gen_be=False)
 
 # hyperparameters from the reference
-args.batch_size = 32
+args.batch_size = 128
 args.backend = 'gpu'
 
 
@@ -30,11 +31,12 @@ if __name__ == '__main__':
 
     # Load the dataset
     # train_set, test_set, nout = get_imdb(args)
-    train_set, test_set, nout, vocab_size = get_saudinet_data(args)
+    (X_train, y_train), (X_test, y_test), nout, vocab_size = get_saudinet_data(args)
+    train_set = ArrayIterator(X_train, y_train, nout)
+    test_set = ArrayIterator(X_test, y_test, nout)
 
     # Build the network
     (encoder, decoder), cost, opt = get_core_net(nout=nout, vocab_size=vocab_size)
-    # model = Model(layers=encoder)
     model = Model(layers=Sequential([encoder, decoder, ]))
 
     callbacks = Callbacks(model, eval_set=test_set, **args.callback_args)

### 2016-04-27 experiment/networks.py
Fixed wrong labels for validation.

@@ -65,7 +65,8 @@ def load_core(embedding_size=128):
     uni = Uniform(low=-0.1/embedding_size, high=0.1/embedding_size)
     enc = Model(SAVE_PATH + 'encoder.neon').layers.layers
     dec = Model(SAVE_PATH + 'decoder.neon').layers.layers
-    return enc, [Linear(embedding_size, uni), ] + dec
+    return enc, dec
+    # return enc, [Linear(embedding_size, uni), ] + dec
 
 
 def save_core(encoder, decoder):
@@ -80,8 +81,7 @@ def get_title_augmentor(vocab_size=20000, embedding_size=128, path=None):
     embedd_size: size of the embedding
     path: filepath from which to load the model's weights
     """
-    embedding_dim = 128
-    uni = Uniform(low=-0.1/embedding_dim, high=0.1/embedding_dim)
+    uni = Uniform(low=1.0, high=1.0)
     glorot = GlorotUniform()
 
     aug = [

### 2016-04-27 experiment/train_augmented.py

@@ -58,12 +58,11 @@ if __name__ == '__main__':
     (X_train_content, y_train_content), (X_test_content, y_test_content), nout, vocab_size = get_saudinet_data(args, modality='content')
     (X_train_title, y_train_title), (X_test_title, y_test_title), nout, vocab_size = get_saudinet_data(args, modality='title')
     train_set = ArrayIterator([X_train_content, X_train_title], y_train_content, nout)
-    test_set = ArrayIterator([X_test_content, X_test_title], y_train_content, nout)
+    test_set = ArrayIterator([X_test_content, X_test_title], y_test_content, nout)
 
     # Build the network
     encoder, decoder = load_core()
     encoder = Sequential(encoder)
-    # decoder = Sequential(decoder)
     augmentor, cost, opt = get_title_augmentor(vocab_size=vocab_size)
     augmentor = Sequential(augmentor)
     model = MultiModalModel(layers=[

### 2016-04-27 experiment/data.py
Made make all work nicely.

@@ -54,7 +54,7 @@ def get_imdb(args):
     """DUmmy dataset for dev."""
     path = load_imdb(path=args.data_dir)
     (X_train, y_train), (X_test, y_test), nclass = pad_data(
-        path, vocab_size=VOCAB_SIZE, sentence_length=SENTENCE_LENGTH)
+        path, vocab_size=20000, sentence_length=SENTENCE_LENGTH)
     train_set = ArrayIterator(X_train, y_train, nclass=2)
     test_set = ArrayIterator(X_test, y_test, nclass=2)
     return (train_set, test_set, 2, 20000)
@@ -67,7 +67,7 @@ downloads the SaudiNewsNet and unzip dataset and returns the folder path
 
 def download_arabic_articles():
     url = "https://codeload.github.com/ParallelMazen/SaudiNewsNet/zip/master"
-    zipfilename = "../SaudiNewsNet.zip"
+    zipfilename = "./SaudiNewsNet.zip"
     folder = zipfilename.replace(".zip", "")
     jsonfolder = os.path.join(folder, "json")
     if not os.path.exists(jsonfolder):
@@ -80,7 +80,7 @@ def download_arabic_articles():
     file = open(zipfilename, "rb")
     z = zipfile.ZipFile(file)
     z.extractall(folder)
-    for subdir, dirs, files in os.walk("../SaudiNewsNet"):
+    for subdir, dirs, files in os.walk("./SaudiNewsNet"):
         for f in files:
             path = os.path.join(subdir, f)
             if ".zip" in path:
@@ -247,5 +247,6 @@ def preprocess_data_train(data, query, path='.', filepath='labeledTrainData.tsv'
 
 
 if __name__ == '__main__':
-    article = load_articles("../SaudiNewsNet")
+    download_arabic_articles()
+    article = load_articles("./SaudiNewsNet")
     fname_h5, fname_vocab = preprocess_data_train(article, 'content')

### 2016-04-27 experiment/networks.py

@@ -53,7 +53,7 @@ def get_core_net(embedding_size=128, vocab_size=20000, nout=10):
     ]
 
     dec = [
-        Dropout(keep=0.7),
+        Dropout(keep=0.5),
         Affine(nout, glorot, bias=glorot, activation=Softmax())
     ]
 

### 2016-04-27 experiment/train_augmented.py

@@ -56,7 +56,7 @@ if __name__ == '__main__':
 
     # Load the dataset
     (X_train_content, y_train_content), (X_test_content, y_test_content), nout, vocab_size = get_saudinet_data(args, modality='content')
-    (X_train_title, y_train_title), (X_test_title, y_test_title), nout, vocab_size = get_saudinet_data(args, modality='title')
+    (X_train_title, y_train_title), (X_test_title, y_test_title), nout, vocab_size = get_saudinet_data(args, modality='authors')
     train_set = ArrayIterator([X_train_content, X_train_title], y_train_content, nout)
     test_set = ArrayIterator([X_test_content, X_test_title], y_test_content, nout)
 

### 2016-04-27 paper/draft.tex
Added Preprocessing, Features, Embedding Layer, Baseline system descriptions to draft.tex

@@
 \documentclass[12pt]{article}
-
-\input{\string~/tex_templates/core}
+\usepackage{amsfonts}
+%\input{\string~/tex_templates/core}
 
@@
 
-\section{Method}\label{method}
+%\section{Method}\label{method}
 
-\subsection{Materials}\label{materials}
+\section{Database}\label{materials}
 
@@
 
-\subsection{Procedure}\label{procedure}
+\section{Procedure}\label{procedure}
 
+\subsection{Data Pre-processing and Features}
+
+Firstly, the UTF-8 encoded data was checked for trailing spaces for removal.
+Next, the data was filtered by removing punctuation symbols, retaining only a subset consisting of \{$,$ $.$ $!$ $($ $)$ $?$\}.
+The data was then split into words which are used as tokens for building the vocabulary and finally obtaining a feature representation for training the neural network.
+A vocabulary is constructed by assigning unique integer word-ids to each unique word appearing in the corpora.
+The punctuations are treated as a separate token and contributes to the vocabulary.
+The url, date and title fields of the corpora were discarded since they were irrelevant for our purpose.
+
+After building the vocabulary for the corpora, the original sentences of the corpora are mapped on a word-basis to obtain a series of integers representing the sentence equivalent which form the features to be input to the embedding layer of the neural network.
+Alternatively, the integer mapping could be replaced with one-hot sparse encoding of each word constituting the sentence.
+The features are shuffled and split for training and testing.
+For efficient data storage and retrieval the features are compressed to HDF5 file format.
+
+\subsection{Neural Network Architecture}
+\subsubsection{Embedding Layer}
+An embedding layer is used to compute a word embedding $W: words \mapsto \mathbb{R}^{n}$ which is a function mapping words of a language to a high dimensional vectors which are continuous, distributed representation of the vocabulary words with good semantic properties.
+The hope of such a representation is to project similar words to similar regions in the hyper-space from a semantic point of view.
+\subsection{Baseline System}
+Two baseline systems are constructed, one to classify the journals based on the content of the articles and the second to classify the journals based on the authors of the articles.
+Identical architectures are used for both the baseline systems.
+The baseline system is a shallow neural network with one hidden Long Short Term Memory (LSTM) layer succeeding the embedding layer.
+The dimension of both the embedding layer and the LSTM was fixed to 128.
+The output layer is a soft-max layer with 14 dimension for each class representing each journal.
+Cross-Entropy loss function was used as an objective function to train the neural network using Adaptive-Gradient (Adagrad).
+
+\subsection{Proposed System}
 The procedure is quite straight-forward. While part of the team worked
@@
 
-\subsection{Evaluation}\label{evaluation}
+\subsection{Evaluation Metrics}\label{evaluation}
 
 \section{Results}\label{results}
-
+\subsection{Baseline}
+\subsection{Proposed System}
 \section{Discussion}\label{discussion}

### 2016-04-28 paper/draft.tex
added core.tex
Added draft of pdf.

@@
 \usepackage{amsfonts}
-%\input{\string~/tex_templates/core}
+\input{\string./core}
 
@@
 
-%\section{Method}\label{method}
-
-\section{Database}\label{materials}
-
+\section{Method}\label{method}
+\subsection{Materials}
 We used the freely available dataset from
@@
 
-\section{Procedure}\label{procedure}
+\subsection{Procedure}\label{procedure}
 
-\subsection{Data Pre-processing and Features}
+\subsubsection{Data Pre-processing and Features}
 
@@
 
-\subsection{Neural Network Architecture}
+%\subsubsection{Neural Network Architecture}
 \subsubsection{Embedding Layer}
@@
 The hope of such a representation is to project similar words to similar regions in the hyper-space from a semantic point of view.
-\subsection{Baseline System}
+
+\subsubsection{Baseline System}
 Two baseline systems are constructed, one to classify the journals based on the content of the articles and the second to classify the journals based on the authors of the articles.
@@
 
-\subsection{Proposed System}
+\subsubsection{Proposed System}
 The procedure is quite straight-forward. While part of the team worked
@@
 
-\subsection{Evaluation Metrics}\label{evaluation}
+\subsection{Evaluation}
 

### 2016-04-28 paper/draft.tex
Slightly reformulated Procedure paragraph for word count.

@@
 
-%\subsubsection{Neural Network Architecture}
 \subsubsection{Embedding Layer}
@@
 
-\subsubsection{Baseline System}
-Two baseline systems are constructed, one to classify the journals based on the content of the articles and the second to classify the journals based on the authors of the articles.
-Identical architectures are used for both the baseline systems.
-The baseline system is a shallow neural network with one hidden Long Short Term Memory (LSTM) layer succeeding the embedding layer.
-The dimension of both the embedding layer and the LSTM was fixed to 128.
-The output layer is a soft-max layer with 14 dimension for each class representing each journal.
-Cross-Entropy loss function was used as an objective function to train the neural network using Adaptive-Gradient (Adagrad).
+\subsubsection{Discriminative Model}
 
-\subsubsection{Proposed System}
-The procedure is quite straight-forward. While part of the team worked
-on building our tailored dataset, the other half worked on the model
-definition and training procedure.
+%\subsubsection{Baseline System}
+We construct two baseline systems, one to classify the journals based on the
+content of the articles and the second on their authors. Identical architectures are used for both the baseline
+systems. The baseline system is a recurrent neural network with one hidden Long
+Short Term Memory (LSTM) layer succeeding the embedding layer. The dimension of
+both the embedding layer and the LSTM was fixed to 128. The output layer is a
+softmax layer with 14 outputs, one per class. The model minimize a cross-entropy loss using adaptive gradient descent. \href{References}{{[}6{]}}
 
-Once every pre-requisite is available, we trained the first encoder
-$E_1$ (implemented as a recurrent neural network) to build the embedding
-$V_1$. Since we only dealt with a relatively simple classification task,
-our decoder $D_1$ was simply a fully connected multi-layer perceptron.
-They were jointly trained end-to-end by propagating the gradients
-through the embedding from $D_1$ to $E_1$.
+%\subsubsection{Proposed System}
+%The procedure is quite straight-forward. While part of the team worked on
+%building our tailored dataset, the other half worked on the model definition
+%and training procedure.
 
-The second training step was to train the second encoder $E_2$. Again,
-we also performed training end-to-end, but specifically did not
-propagate the gradients through $E_1$.
+%Once every pre-requisite is available, we trained the first encoder $E_1$
+%(implemented as a recurrent neural network) to build the embedding $V_1$. Since
+%we only dealt with a relatively simple classification task, our decoder $D_1$
+%was simply a fully connected multi-layer perceptron. They were jointly trained
+%end-to-end by propagating the gradients through the embedding from $D_1$ to
+%$E_1$.
+
+%The second training step was to train the second encoder $E_2$. Again, we also
+%performed training end-to-end, but specifically did not propagate the gradients
+%through $E_1$.
 
@@
 \subsection{Proposed System}
+
 \section{Discussion}\label{discussion}
 
-\section{References}\label{references}
+\section{References}\label{References}
 
@@
   Karpathy \& al, https://cs.stanford.edu/people/karpathy/nips2014.pdf
+
+\item Adaptive Subgradient Methods for Online Learning and Stochastic Optimization, Ducih \& al, http://www.jmlr.org/papers/volume12/duchi11a/duchi11a.pdf
 \end{enumerate}

### 2016-04-28 paper/draft.tex
Added two paragraphs on evaluation procedure.

@@
 \subsection{Evaluation}
+The evaluation procedure for all experiments is based on the classification accuracy of each statistical model on a held-out validation set.
+
+Before any learning happens, we begin by partitioning the dataset in two subsets: training and test.
+This split is achieved by first loading the entire dataset in memory and assigning the first 80\% examples to the validation set and the remaining 20\% to the test set.
+Doing so, we increase our confidence in the resulting accuracy.
+In preliminary experiments we observed that the majority of the models were highly overfitting the training set.
+In order to find better hyperparameters, we thus further partitioned the training set into a development and a validation set.
+(again an 80-20 split) Once the recall-variance trade-off reached a satisfactory level on the development and validation set, we train all models using the same hyperparameters on the entire (identical) training set, and evaluate them on the test set.
+
+The training for evaluation is performed as follows. We begin by training a single encoder and the decoder on a single modality.
+(eg, the content of the articles) We measure the obtained accuracy on the test set and serialize the model's parameters on disk.
+In the second step, we recreate the previously trained encoder and decoder, and initialize them with their respective serialized parameters.
+We also instantiate a new encoder architecturally identical to the first one but with untrained parameters.
+Finally, we load both the previous and the new modality from the dataset and their corresponding labels, before proceeding to the training steps as described in the previous sections.
+
+Paragraph: By using a standardized ds, we can fairly compare models...
 
 \section{Results}\label{results}
+
+Needs results for:
+
+1. single model on authors
+2. single model on content
+3. single model on titles
+4. multimodal on authors-content
+5. multimodal on title-content
+6. ? multimodal author-titles ?
+
 \subsection{Baseline}

### 2016-04-28 paper/draft.tex
More on embedding, switched to RecurrentMean instead.

@@
 
+\begin{figure}[htbp]
+\centering
+\includegraphics{figs/multimodal.png}
+\caption{Multi-modal Transfer Learning}
+\end{figure}
+
 Although we could have used any kind of mapping, we chose to use deep
@@
 
+We tried two approaches when building the vector embedding from multiple modalities.
+The first one was to vertically stack the different embeddings from the different encoders and learn the actual embedding from a linear combination from this higher dimensional vector.
+This led to poor results and we instead decided to experiment with both the summing over every embedding, as well as taking their mean in each dimension.
+
 \subsubsection{Discriminative Model}
@@
 
-Paragraph: By using a standardized ds, we can fairly compare models...
-
 \section{Results}\label{results}
@@
 
-\subsection{Baseline}
-\subsection{Proposed System}
+TODO: Say if we ended up using RecurrentSum or RecurrentMean for the embedding. (see embedding layer section)
 

### 2016-04-28 experiment/data.py
experimental changes.  #Please enter the commit message for your changes. Lines starting

@@ -19,7 +19,7 @@ from neon.data import ArrayIterator
 from neon.data.dataloaders import load_imdb
 from neon.data.text_preprocessing import pad_data
 
-SENTENCE_LENGTH = 128
+SENTENCE_LENGTH = 2048
 
 
 def get_saudinet_data(args, modality='content'):

### 2016-04-28 experiment/networks.py

@@ -53,7 +53,7 @@ def get_core_net(embedding_size=128, vocab_size=20000, nout=10):
     ]
 
     dec = [
-        Dropout(keep=0.5),
+        Dropout(keep=0.05),
         Affine(nout, glorot, bias=glorot, activation=Softmax())
     ]
 

### 2016-04-28 experiment/train_augmented.py

@@ -24,7 +24,7 @@ parser = NeonArgparser(__doc__)
 args = parser.parse_args(gen_be=False)
 
 # hyperparameters from the reference
-args.batch_size = 32
+args.batch_size = 128
 args.backend = 'gpu'
 
 

### 2016-04-28 paper/draft.tex
a folder for figures

--- 2016-04-28 paper/draft.tex
@@
 
-\section{Method}\label{method}
-\subsection{Materials}
+%\section{Method}\label{method}
+
+\section{Database}\label{materials}
+
 We used the freely available dataset from
 \url{https://github.com/ParallelMazen/SaudiNewsNet} The dataset contains
-a total of 31,030 Arabic newspaper articles, with title, author, date,
-url and content in each entry. Article objects are reprensented in json
+a total of 31,030 Arabic newspaper articles. Article objects are reprensented in json
 format, with UTF-8 encoding. We wrote a script to download the data from
-github repo, unzip each file, and read them in as json objects. The
-function can also give out content by key values such as title, author
-and etc.
+github repo, unzip each file, and read them in as json objects. Each json object 
+contains the flollowing fields:
+source: A string identified of the newspaper from which the article was extracted. It can have one of the following values:
+\begin{itemize}
+\item source: A string identifier of the newspaper from which the article was extracted.
+\item url: The full URL from which the article was extracted.
+\item date\_extracted: The timestamp of the date on which the article was extracted. It has the format YYYY-MM-DD hh:mm:ss. 
+\item title: The title of the article. 
+\item author: The author of the article.
+\item content: The content of the article.
+\end{itemize}
 
-\subsection{Procedure}\label{procedure}
+\section{Procedure}\label{procedure}
 
-\subsubsection{Data Pre-processing and Features}
+\subsection{Data Pre-processing and Features}
 
@@
 
+\subsection{Neural Network Architecture}
 \subsubsection{Embedding Layer}
@@
 The hope of such a representation is to project similar words to similar regions in the hyper-space from a semantic point of view.
+\subsection{Baseline System}
+Two baseline systems are constructed, one to classify the journals based on the content of the articles and the second to classify the journals based on the authors of the articles.
+Identical architectures are used for both the baseline systems.
+The baseline system is a shallow neural network with one hidden Long Short Term Memory (LSTM) layer succeeding the embedding layer.
+The dimension of both the embedding layer and the LSTM was fixed to 128.
+The output layer is a soft-max layer with 14 dimension for each class representing each journal.
+Cross-Entropy loss function was used as an objective function to train the neural network using Adaptive-Gradient (Adagrad).
 
-\subsubsection{Discriminative Model}
+\subsection{Proposed System}
+The procedure is quite straight-forward. While part of the team worked
+on building our tailored dataset, the other half worked on the model
+definition and training procedure.
 
-%\subsubsection{Baseline System}
-We construct two baseline systems, one to classify the journals based on the
-content of the articles and the second on their authors. Identical architectures are used for both the baseline
-systems. The baseline system is a recurrent neural network with one hidden Long
-Short Term Memory (LSTM) layer succeeding the embedding layer. The dimension of
-both the embedding layer and the LSTM was fixed to 128. The output layer is a
-softmax layer with 14 outputs, one per class. The model minimize a cross-entropy loss using adaptive gradient descent. \href{References}{{[}6{]}}
+Once every pre-requisite is available, we trained the first encoder
+$E_1$ (implemented as a recurrent neural network) to build the embedding
+$V_1$. Since we only dealt with a relatively simple classification task,
+our decoder $D_1$ was simply a fully connected multi-layer perceptron.
+They were jointly trained end-to-end by propagating the gradients
+through the embedding from $D_1$ to $E_1$.
 
-%\subsubsection{Proposed System}
-%The procedure is quite straight-forward. While part of the team worked on
-%building our tailored dataset, the other half worked on the model definition
-%and training procedure.
+The second training step was to train the second encoder $E_2$. Again,
+we also performed training end-to-end, but specifically did not
+propagate the gradients through $E_1$.
 
-%Once every pre-requisite is available, we trained the first encoder $E_1$
-%(implemented as a recurrent neural network) to build the embedding $V_1$. Since
-%we only dealt with a relatively simple classification task, our decoder $D_1$
-%was simply a fully connected multi-layer perceptron. They were jointly trained
-%end-to-end by propagating the gradients through the embedding from $D_1$ to
-%$E_1$.
-
-%The second training step was to train the second encoder $E_2$. Again, we also
-%performed training end-to-end, but specifically did not propagate the gradients
-%through $E_1$.
-
-\subsection{Evaluation}
+\subsection{Evaluation Metrics}\label{evaluation}
 
@@
 \subsection{Proposed System}
-
 \section{Discussion}\label{discussion}
 
-\section{References}\label{References}
+\section{References}\label{references}
 
@@
   Karpathy \& al, https://cs.stanford.edu/people/karpathy/nips2014.pdf
-
-\item Adaptive Subgradient Methods for Online Learning and Stochastic Optimization, Ducih \& al, http://www.jmlr.org/papers/volume12/duchi11a/duchi11a.pdf
 \end{enumerate}

### 2016-04-28 paper/draft.tex

--- 2016-04-28 paper/draft.tex
@@
 \url{https://github.com/ParallelMazen/SaudiNewsNet} The dataset contains
-a total of 31,030 Arabic newspaper articles, with title, author, date,
-url and content in each entry. Article objects are reprensented in json
+a total of 31,030 Arabic newspaper articles. Article objects are reprensented in json
 format, with UTF-8 encoding. We wrote a script to download the data from
-github repo, unzip each file, and read them in as json objects. The
-function can also give out content by key values such as title, author
-and etc.
+github repo, unzip each file, and read them in as json objects. Each json object 
+contains the flollowing fields:
+source: A string identified of the newspaper from which the article was extracted. It can have one of the following values:
+\begin{itemize}
+\item source: A string identifier of the newspaper from which the article was extracted.
+\item url: The full URL from which the article was extracted.
+\item date\_extracted: The timestamp of the date on which the article was extracted. It has the format YYYY-MM-DD hh:mm:ss. 
+\item title: The title of the article. 
+\item author: The author of the article.
+\item content: The content of the article.
+\end{itemize}
 

### 2016-04-28 experiment/data.py
update data.py
update data.py to deal with simultaneously loading data in multi-model

@@ -30,7 +30,8 @@ def get_saudinet_data(args, modality='content'):
     """ Returns a train and validation dataset from SaudiNewsNet. """
     # get the preprocessed and tokenized data
     article = load_articles("./SaudiNewsNet")
-    fname_h5, fname_vocab = preprocess_data_train(article, modality, './labeledTrainData.tsv')
+    filepath = './' + modality + '_labledTraindata.tsv'
+    fname_h5, fname_vocab = preprocess_data_train(article, modality, filepath=filepath)
 
     h5f = h5py.File(fname_h5, 'r')
     data, h5train, h5valid = h5f['data'], h5f['train'], h5f['valid']

### 2016-04-28 experiment/networks.py
update networks.py
update networks.py to deal with dynamic parameter setting

@@ -22,10 +22,11 @@ from neon.transforms import (
     Logistic,
     Softmax,
     CrossEntropyMulti,
+    Explin,
+    Normalizer,
 )
 
 
-SAVE_PATH = './saved_models/'
 
 
 def get_cost_opt():
@@ -35,25 +36,35 @@ def get_cost_opt():
     return cost, opt
 
 
-def get_core_net(embedding_size=128, vocab_size=20000, nout=10):
+def get_core_net(embedding_size=128, vocab_size=20000, nout=10, dropout_rate = 0.5, activation_function = 1):
     """
     Returns a tuple containing the original encoder and decoder networks.
     embedd_size: size of the output of the encoder
     nout: size of the output of the decoder
     path: filepath from which the weights should be loaded
     """
-    embedding_dim = 128
+    if activation_function == 1:
+        af = Tanh()
+    if activation_function == 2:
+        af = Explin(alpha=0)
+    if activation_function == 3:
+        af = Logistic()
+    if activation_function == 4:
+        af = Normalizer()
+
+    
+    embedding_dim = embedding_size
     uni = Uniform(low=-0.1/embedding_dim, high=0.1/embedding_dim)
     glorot = GlorotUniform()
 
     enc = [
         LookupTable(vocab_size=vocab_size, embedding_dim=embedding_dim, init=uni, pad_idx=0, update=True),
-        LSTM(embedding_size, glorot, activation=Tanh(), gate_activation=Logistic(), reset_cells=True),
+        LSTM(embedding_size, glorot, activation=af, gate_activation=Logistic(), reset_cells=True),
         RecurrentSum(),
     ]
 
     dec = [
-        Dropout(keep=0.5),
+        Dropout(keep=dropout_rate),
         Affine(nout, glorot, bias=glorot, activation=Softmax())
     ]
 
@@ -61,17 +72,15 @@ def get_core_net(embedding_size=128, vocab_size=20000, nout=10):
     return (enc, dec), cost, opt
 
 
-def load_core(embedding_size=128):
-    uni = Uniform(low=-0.1/embedding_size, high=0.1/embedding_size)
-    enc = Model(SAVE_PATH + 'encoder.neon').layers.layers
-    dec = Model(SAVE_PATH + 'decoder.neon').layers.layers
+def load_core(file_prefix,embedding_size=128):
+    enc = Model(file_prefix + '_encoder.neon').layers.layers
[…]

### 2016-04-28 experiment/train_augmented.py
update train_augmented.py
update train_augmented.py to deal with dynamic parameter setting

@@ -19,14 +19,6 @@ from neon.layers import RecurrentSum, RecurrentMean
 from networks import load_core, get_title_augmentor
 from data import get_imdb, get_saudinet_data
 
-# parse the command line arguments
-parser = NeonArgparser(__doc__)
-args = parser.parse_args(gen_be=False)
-
-# hyperparameters from the reference
-args.batch_size = 32
-args.backend = 'gpu'
-
 
 class MultiModalModel(Model):
 
@@ -51,17 +43,66 @@ class MultiModalModel(Model):
 
 
 if __name__ == '__main__':
+    # parse the command line arguments
+    parser = NeonArgparser(__doc__)
+    parser.add_argument("new_data_source", help = "choose the data source used for classification. options: content, title, author, author-content, author-title, content-title")
+    parser.add_argument("initial_model", help = "choose the initial encoder-decoder model. options: content, title, author")
+    
+
+    args = parser.parse_args(gen_be=False)
+
+    # hyperparameters from the reference
+    args.batch_size = 32
+    args.backend = 'gpu'
+    
+    print ' '
+    print "new source used for classification is: ", args.new_data_source
+    print "initial model is trained on: ", args.initial_model
+    print ' '
+    
+    
     # Setup backend
     be = gen_backend(**extract_valid_args(args, gen_backend))
 
     # Load the dataset
     (X_train_content, y_train_content), (X_test_content, y_test_content), nout, vocab_size = get_saudinet_data(args, modality='content')
-    (X_train_title, y_train_title), (X_test_title, y_test_title), nout, vocab_size = get_saudinet_data(args, modality='authors')
-    train_set = ArrayIterator([X_train_content, X_train_title], y_train_content, nout)
-    test_set = ArrayIterator([X_test_content, X_test_title], y_test_content, nout)
+    (X_train_title, y_train_title), (X_test_title, y_test_title), nout, vocab_size = get_saudinet_data(args, modality='title')
+    (X_train_authors, y_train_authors), (X_test_authors, y_test_authors), nout, vocab_size = get_saudinet_data(args, modality='author')
+    
+    
+    X_train, X_test = {}, {}
+    X_train['content-author'], X_test['content-author'] = [X_train_content,X_train_authors], [X_test_content,X_test_authors]
+    X_train['content-title'], X_test['content-title'] = [X_train_content,X_train_title], [X_test_content,X_test_title]
+    
[…]

### 2016-04-28 paper/draft.tex
insert figure for article-newspaper distribution

@@
 \url{https://github.com/ParallelMazen/SaudiNewsNet} The dataset contains
-a total of 31,030 Arabic newspaper articles. Article objects are reprensented in json
-format, with UTF-8 encoding. We wrote a script to download the data from
+a total of 31,030 Arabic newspaper articles, with a total number of 8,758,976 words.
+
+\begin{figure}
+\centering
+\includegraphics[width=\textwidth]{figures/article-newspaper_distribution.png}
+\caption{Figure shows article-newspaper distribution}
+\end{figure}
+
+Article objects are reprensented in json format, with UTF-8 encoding. We wrote a script to download the data from
 github repo, unzip each file, and read them in as json objects. Each json object 

### 2016-04-28 paper/draft.tex
fixed to use bibtex

@@
 natural language tasks. Learning embeddings has been previously done by
-\href{References}{{[}1{]}}, although our proposed contribution is
-slightly different. \href{References}{{[}1{]}} used deep autoencoders to
+\cite{zhuang2015supervised}, although our proposed contribution is
+slightly different. \cite{zhuang2015supervised} used deep autoencoders to
 obtain a better initialization of the parameters of their model. Our
 approach instead is much closer in spirit to the work of Sutskever
-\href{References}{{[}3{]}} and Vinyals \href{References}{{[}4{]}}. They
+\cite{sutskever2014sequence} and Vinyals \cite{vinyals2015grammar}. They
 both use encoders on a sequence of data to generate a
@@
 component to their contribution. This approach is also similar to the
-work of Karpathy \& al \href{References}{{[}5{]}} where they mapped
+work of Karpathy \& al \cite{karpathy2014deep} where they mapped
 images to their captions with embeddings.
@@
 both the embedding layer and the LSTM was fixed to 128. The output layer is a
-softmax layer with 14 outputs, one per class. The model minimize a cross-entropy loss using adaptive gradient descent. \href{References}{{[}6{]}}
+softmax layer with 14 outputs, one per class. The model minimize a cross-entropy loss using adaptive gradient descent. \cite{duchi2011adaptive}
 
@@
 
-\section{References}\label{References}
-
-Part of the relevant literature review. More literature was involved for
-the deep learning part.
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\item
-  Supervised Representation Learning: Transfer Learning with Deep
-  Autoencoders, Zhuang \& al,
-  http://ijcai.org/Proceedings/15/Papers/578.pdf
-\item
-  Transfer Learning via Dimensionality Reduction, Pan \& al,
-
-  https://www.cse.ust.hk/\textasciitilde{}jamesk/papers/aaai08.pdf
-\item
-  Sequence to Sequence Learning with Neural Networks, Sutskever \& al,
-
-  http://arxiv.org/abs/1409.3215
-\item
-  Grammar as a Foreign Language, Vinyals \& al,
-  http://arxiv.org/abs/1412.7449
-\item
-  Deep Fragment Embeddings for Bidirectional Image Sentence Mapping,
-  Karpathy \& al, https://cs.stanford.edu/people/karpathy/nips2014.pdf
-
-\item Adaptive Subgradient Methods for Online Learning and Stochastic Optimization, Ducih \& al, http://www.jmlr.org/papers/volume12/duchi11a/duchi11a.pdf
-\end{enumerate}
+\bibliography{reference} 
+\bibliographystyle{ieeetr}
 

### 2016-04-28 experiment/networks.py
Fixed a merge conflict and removed buggy code.

@@ -73,7 +73,7 @@ def get_core_net(embedding_size=128, vocab_size=20000, nout=10, dropout_rate = 0
     return (enc, dec), cost, opt
 
 
-def load_core(file_prefix,embedding_size=128):
+def load_core(file_prefix, embedding_size=128):
     enc = Model(file_prefix + '_encoder.neon').layers.layers
     dec = Model(file_prefix + '_decoder.neon').layers.layers
     return enc, dec

### 2016-04-28 experiment/train_augmented.py

@@ -45,68 +45,25 @@ class MultiModalModel(Model):
 if __name__ == '__main__':
     # parse the command line arguments
     parser = NeonArgparser(__doc__)
-    parser.add_argument("new_data_source", help = "choose the data source used for classification. options: content, title, author, author-content, author-title, content-title")
-    parser.add_argument("initial_model", help = "choose the initial encoder-decoder model. options: content, title, author")
-
-
     args = parser.parse_args(gen_be=False)
 
     # hyperparameters from the reference
     args.batch_size = 32
     args.backend = 'gpu'
-
-    print ' '
-    print "new source used for classification is: ", args.new_data_source
-    print "initial model is trained on: ", args.initial_model
-    print ' '
-
+    modal1 = 'content'
+    modal2 = 'authors'
 
     # Setup backend
     be = gen_backend(**extract_valid_args(args, gen_backend))
 
     # Load the dataset
-    (X_train_content, y_train_content), (X_test_content, y_test_content), nout, vocab_size = get_saudinet_data(args, modality='content')
-    (X_train_title, y_train_title), (X_test_title, y_test_title), nout, vocab_size = get_saudinet_data(args, modality='title')
-<<<<<<< HEAD
+    (X_train_content, y_train_content), (X_test_content, y_test_content), nout, vocab_size = get_saudinet_data(args, modality=modal1)
+    (X_train_title, y_train_title), (X_test_title, y_test_title), nout, vocab_size = get_saudinet_data(args, modality=modal2)
     train_set = ArrayIterator([X_train_content, X_train_title], y_train_content, nout)
     test_set = ArrayIterator([X_test_content, X_test_title], y_test_content, nout)
-=======
-    (X_train_authors, y_train_authors), (X_test_authors, y_test_authors), nout, vocab_size = get_saudinet_data(args, modality='author')
-
-
-    X_train, X_test = {}, {}
-    X_train['content-author'], X_test['content-author'] = [X_train_content,X_train_authors], [X_test_content,X_test_authors]
-    X_train['content-title'], X_test['content-title'] = [X_train_content,X_train_title], [X_test_content,X_test_title]
-
-    X_train['title-author'], X_test['title-author'] = [X_train_title,X_train_authors], [X_test_title, X_test_authors]
-    X_train['title-content'], X_test['title-content'] = [X_train_title,X_train_content], [X_test_title, X_test_content]
-
[…]

### 2016-04-28 experiment/train_core.py

@@ -23,38 +23,23 @@ import argparse
 if __name__ == '__main__':
     #parse parameter settings from command line
     parser = NeonArgparser(__doc__)
-    parser.add_argument("data_source", help="choose the data source to train initial encoder-decoder. defaul is content")
-    parser.add_argument("-lr", "--learning_rate", type = float, help="set the learning rate. defaul 0.01")
-    parser.add_argument("-es", "--embedding_size", type = int, help = "set the embedding size. default 128")
-    parser.add_argument("-dr", "--dropout_rate", type = float, help = "set the dropout rate. default 0.5")
-    parser.add_argument("-af", "--activation_function", type = int, help = "set the activation default: Tanh; 1: Tanh, 2: ReLU, 3: Sigmoid, 4: Normalizer")
-    
+    # parser.add_argument("data_source", help="choose the data source to train initial encoder-decoder. defaul is content")
+    # parser.add_argument("-lr", "--learning_rate", type = float, help="set the learning rate. defaul 0.01")
+    # parser.add_argument("-es", "--embedding_size", type = int, help = "set the embedding size. default 128")
+    # parser.add_argument("-dr", "--dropout_rate", type = float, help = "set the dropout rate. default 0.5")
+    # parser.add_argument("-af", "--activation_function", type = int, help = "set the activation default: Tanh; 1: Tanh, 2: ReLU, 3: Sigmoid, 4: Normalizer")
+
     args = parser.parse_args(gen_be=False)
 
     # hyperparameters from the reference
     args.batch_size = 128
     args.backend = 'gpu'
-    
-    
-    if args.learning_rate:
-        learning_rate = args.learning_rate
-    else:
-        learning_rate = 0.01
-    
-    if args.embedding_size:
-        embedding_size = args.embedding_size
-    else:
-        embedding_size = 128
-    
-    if args.dropout_rate:
-        dropout_rate = args.dropout_rate
-    else:
-        dropout_rate = 0.5
-    
-    if args.activation_function:
-        activation_function = args.activation_function
-    else:
-        activation_function = 1
+
+    modality = 'content'
+    learning_rate = 0.01
+    embedding_size = 128
+    dropout_rate = 0.5
+    activation_function = 1
 
     af={}
     af[1] = 'Tanh'
@@ -63,7 +48,7 @@ if __name__ == '__main__':
     af[4] = 'Normalizer'
 
     print ' '
[…]

### 2016-04-29 paper/draft.tex
Added image of architecture.
update draft
update draft. modifications include:
rewrite the abstract section and the first and second paragraphs of
introduction section. Feel free to change them if you think another way
is better.

@@
 \begin{abstract}
-In this short paper we propose an approach to transfer learning using rich
-vector embeddings. The suggested technique can be applied to any supervised
-task, and it handles multiple sources and changing sources of data without the
-need for retraining. To verify our ideas, we apply our ideas to the task of
-text-classification.
+%In this short paper we propose an approach to transfer learning using rich
+%vector embeddings. The suggested technique can be applied to any supervised
+%task, and it handles multiple sources and changing sources of data without the
+%need for retraining. To verify our ideas, we apply our ideas to the task of
+%text-classification.
+
+In this short paper, we propose a Modular Deep Encoder-Decoder network (MDED) for text classification.
+The basic idea behind MDED is to extend a pre-trained model, which consists of a set of deep encoder-decoders, with an additional source of data by adding a new encoder to the network.
+MDED has been applied to text classification on SaudiNewsNet.
+A modular Long Short Term Memory (LSTM) network is built.
+Experimental results show that our algorithm can efficiently combine new source of data and pre-trained model.
+(show some summaries of experimental results here)
+
 \end{abstract}
@@
 
-Our goal is to generate rich vector embeddings from articles to classify
-them into predefined categories. Then, we want to extend our model with
-an additional source of data: the title of the videos. To handle this
-new knowledge source without retraining our previous model, we suggest
-to generate a new embedding that will be used to modify the original
-one. This combined embedding will then be used for the classification
-task.
+%Our goal is to generate rich vector embeddings from articles to classify
+%them into predefined categories. Then, we want to extend our model with
+%an additional source of data: the title of the videos. To handle this
+%new knowledge source without retraining our previous model, we suggest
+%to generate a new embedding that will be used to modify the original
+%one. This combined embedding will then be used for the classification
+%task.
+
+In the past decade, deep learning has been successfully applied to natural language processing (NLP).
+It has been shown that end-to-end trained deep learning algorithms can outperform traditional algorithms on various NLP tasks.
+
+However, the training process of deep learning algorithms is usually very time-consuming.
+And it is inefficient to update a model and re-train it from scratch everytime there is a new data source coming.
+To alleviate this problem, a novel Modular Deep Encoder-Decoder network (MDED) is proposed in this paper.
+The basic idea behind MDED is to extend a pre-trained model, which consists of a set of deep encoder-decoders, with an additional source of data by adding a new encoder to the network.
 
@@
 \centering
-\includegraphics{figs/multimodal.png}
+\includegraphics{figures/multimodal.png}
 \caption{Multi-modal Transfer Learning}
@@
 
-\begin{figure}
+\begin{figure}[h!]
 \centering
@@
 
-Needs results for:
+\subsection{Single LSTM network}
 
-1. single model on authors
-2. single model on content
-3. single model on titles
-4. multimodal on authors-content
-5. multimodal on title-content
-6. ? multimodal author-titles ?
+First, three single LSTM networks are trained for text classification, where title, author and content values are used for training data, respectively.
+The classification performance of them are reported in Table.\ref{single_lstm_acc}.
+From Table.\ref{single_lstm_acc} we can see that xxx model has the best classification performance among these three models.
 
-TODO: Say if we ended up using RecurrentSum or RecurrentMean for the embedding. (see embedding layer section)
+\begin{table}[!t]
+\begin{center}
+\caption{Classification performance of single LSTM network}
+\label{single_lstm_acc}
+\begin{tabular}{c|c|c|c}
+\hline
+Training data & Title & Author & Content\\
+\hline
+
+Training accuracy &  &  &  \\
+
+Testing accuracy & & & \\
+
+\hline
+\end{tabular}
+\end{center}
+\end{table}
+
+Moreover, the training behavior of these three models are presented in Fig.\ref{training_loss_single}.
+
+\begin{figure}[!t]
+\begin{center}
+%\includegraphics[width=2.8in]{path_sample.eps}
+\end{center}
+\caption{Training loss and testing loss of single LSTM networks.}
+\label{training_loss_single}
+\end{figure}
+
+\subsection{Modular LSTM network}
+
+In oder to further improve the classification performance, new sources of training data are added to the base single LSTM network.
+For each single LSTM network, two other data source are added to it, respectively.
+For example, for content LSTM network, author of the articles and title of the articles are added to it as an additional source of training data.
+Technically, a new encoder is added to the original LSTM network.
+Performance of these modular LSTM networks are reported in Table.\ref{modular_lstm_acc}.
+
+\begin{table}[!t]
+\begin{center}
+\caption{Classification performance of modular LSTM networks}
+\label{modular_lstm_acc}
+\begin{tabular}{c|cc|cc|cc}
+\hline
+
+Base source & \multicolumn{2}{c}{Title} & \multicolumn{2}{c}{Content} & \multicolumn{2}{c}{Author} \\
+\hline
+New source   &   Content   &   Author     &       Title  & Author                &            Content & Title \\
+\hline
+Training acc   &                   &                  &                &                           &                           & \\
+Tesging acc   &                   &                  &                &                           &                           & \\
+
+\hline
+
+\hline
+\end{tabular}
+\end{center}
+\end{table}
+
+Moreover, the training behavior of them are presented in Fig.\ref{training_loss_modular}.
+
+\begin{figure}[!t]
+\begin{center}
+%\includegraphics[width=2.8in]{path_sample.eps}
+\end{center}
+\caption{Training loss and testing loss of modular LSTM networks.}
+\label{training_loss_modular}
+\end{figure}
+
+%Needs results for:
+
+%1. single model on authors
+%2. single model on content
+%3. single model on titles
+%4. multimodal on authors-content
+%5. multimodal on title-content
+%6. ? multimodal author-titles ?
+
+%TODO: Say if we ended up using RecurrentSum or RecurrentMean for the embedding. (see embedding layer section)
 

### 2016-04-29 experiment/train_augmented.py

@@ -57,10 +57,53 @@ if __name__ == '__main__':
     be = gen_backend(**extract_valid_args(args, gen_backend))
 
     # Load the dataset
+<<<<<<< Updated upstream
     (X_train_content, y_train_content), (X_test_content, y_test_content), nout, vocab_size = get_saudinet_data(args, modality=modal1)
     (X_train_title, y_train_title), (X_test_title, y_test_title), nout, vocab_size = get_saudinet_data(args, modality=modal2)
     train_set = ArrayIterator([X_train_content, X_train_title], y_train_content, nout)
     test_set = ArrayIterator([X_test_content, X_test_title], y_test_content, nout)
+=======
+    (X_train_content, y_train_content), (X_test_content, y_test_content), nout, vocab_size = get_saudinet_data(args, modality='content')
+    (X_train_title, y_train_title), (X_test_title, y_test_title), nout, vocab_size = get_saudinet_data(args, modality='title')
+    (X_train_authors, y_train_authors), (X_test_authors, y_test_authors), nout, vocab_size = get_saudinet_data(args, modality='author')
+    
+    
+    X_train, X_test = {}, {}
+    X_train['content-author'], X_test['content-author'] = [X_train_content,X_train_authors], [X_test_content,X_test_authors]
+    X_train['content-title'], X_test['content-title'] = [X_train_content,X_train_title], [X_test_content,X_test_title]
+    
+    X_train['title-author'], X_test['title-author'] = [X_train_title,X_train_authors], [X_test_title, X_test_authors]
+    X_train['title-content'], X_test['title-content'] = [X_train_title,X_train_content], [X_test_title, X_test_content]
+    
+    X_train['author-content'], X_test['author-content'] = [X_train_authors, X_train_content], [X_test_authors, X_test_content]
+    X_train['author-title'], X_test['author-title'] = [X_train_authors, X_train_title], [X_test_authors, X_test_title]
+
+    X_train['content-author-title'], X_test['content-author-title'] = [X_train_content,X_train_authors,X_train_title], [X_test_content,X_test_authors,X_test_title]
+
+    X_train['title-author-content'], X_test['title-author-content'] = [X_train_title,X_train_authors,X_train_content], [X_test_title, X_test_authors,X_test_content]
+
[…]

### 2016-04-29 paper/draft.tex
Changed structure; Title structure; Removed Evaluation content; updated content under Materials; Added figures for data distribution and sentence lengths

@@
-\author{Group 40: Arnold, Gurunat, Huang, \& Qu}
 \title{Modular Deep Encoder-Decoders}
-\date{\today}
+\author{Sebastian Arnold\Mark{1}, Prashanth Gurunath Shivakumar\Mark{2}, Cheng Qu\Mark{3}\\ and Qiangui Huang\Mark{4}}
+%\affil[1]{Department of Computer Science, University of Southern California, Los Angeles, CA \authorcr Email: {\tt \{arnolds, chengqu, qianguih\}@usc.edu}\vspace{1.5ex}}
+%\affil[2]{Ming Hsieh Department of Electrical Engineering, University of Southern California, Los Angeles, CA \authorcr Email: {\tt pgurunat@usc.edu} \vspace{-2ex}}
+
 \documentclass[12pt]{article}
@@
 
+\newcommand\Mark[1]{\textsuperscript#1}
+
 % Custom Title
-
-%\def\maketitle{
-    %\centering
-    %\par\textbf{\LARGE\@title}
-    %\par\hfill
-    %\par{\@author, \@date}
-    %\par\hfill
-    %\par\hfill
-    %\rule{\textwidth}{3pt}
-%}
-
 \def\maketitle{
-    \begin{centering}
 	\par\rule{\textwidth}{2pt}
 	\par\hfill
-    \par\textbf{\LARGE\@title}
-    \par\hfill
-    \par{\textit{\@author}}
-    \par\hfill
-    \par{\@date}
+	\begin{centering}
+	\begingroup
+	\centering
+	{\par\textbf{\LARGE\@title}\\[1.5em]
+	\large\par{\textit{\@author}}}\\[1em]
+	\begin{tabular}{*{4}{>{\centering}p{.23\textwidth}}}
+	\url{arnolds@usc.edu}\Mark{1} & \url{pgurunat@usc.edu}\Mark{2} & \url{chengqu@usc.edu}\Mark{3} & \url{qianguih@usc.edu}\Mark{4} \tabularnewline
+	9013085897 & 2251924199 & 9532576000 & 2385279985
+	\end{tabular}\par
+	\endgroup
 	\par\rule{\textwidth}{2pt}
@@
 
-Article objects are reprensented in json format, with UTF-8 encoding. We wrote a script to download the data from
-github repo, unzip each file, and read them in as json objects. Each json object 
-contains the flollowing fields:
-source: A string identified of the newspaper from which the article was extracted. It can have one of the following values:
+Article objects are represented in json format, with UTF-8 encoding.
+We wrote a script to download the data from github repo, unzip each file, and read them in as json objects.
+Each json object contains the following fields:
+
 \begin{itemize}
@@
 \end{itemize}
+
+The dataset is partitioned into training, development and testing subsets.
+80\% of the data is assigned for training and 10\% for development and testing.
+The development set is utilized for hyper-parameter tuning and the results are finally presented on the testing set.
+During partitioning, care is taken to ensure appropriate percentage of data is seen in all the classes.
+Figure~\ref{fig:dist} shows the distribution of data used for training and testing in each class.
+Figure~\ref{fig:sent_dist} shows the distribution of sentence lengths of the content of the articles.
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=\textwidth]{figures/test_class_distribution.png}
+\caption{Distribution of data for training and testing}\label{fig:dist}
+\end{figure}
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=\textwidth,height=6cm]{figures/sentence_length.png}
+\caption{Distribution of data for training and testing}\label{fig:sent_dist}
+\end{figure}
 
@@
 
-\subsubsection{Discriminative Model}
+%\subsubsection{Discriminative Model}
 
-%\subsubsection{Baseline System}
+\subsubsection{Baseline System}
 We construct two baseline systems, one to classify the journals based on the
 content of the articles and the second on their authors. Identical architectures are used for both the baseline
-systems. The baseline system is a recurrent neural network with one hidden Long
-Short Term Memory (LSTM) layer succeeding the embedding layer. The dimension of
-both the embedding layer and the LSTM was fixed to 128. The output layer is a
-softmax layer with 14 outputs, one per class. The model minimize a cross-entropy loss using adaptive gradient descent. \cite{duchi2011adaptive}
+systems.
+The baseline system is a recurrent neural network with one hidden Long Short Term Memory (LSTM) layer succeeding the embedding layer.
+The dimension of both the embedding layer and the LSTM was fixed to 128.
+The output layer is a softmax layer with 14 outputs, one per class.
+The model minimize a cross-entropy loss using adaptive gradient descent.
+\cite{duchi2011adaptive}
 
-%\subsubsection{Proposed System}
+\subsubsection{Proposed System}
+The training for evaluation is performed as follows. We begin by training a single encoder and the decoder on a single modality.
+(eg, the content of the articles) We measure the obtained accuracy on the test set and serialize the model's parameters on disk.
+In the second step, we recreate the previously trained encoder and decoder, and initialize them with their respective serialized parameters.
+We also instantiate a new encoder architecturally identical to the first one but with untrained parameters.
+Finally, we load both the previous and the new modality from the dataset and their corresponding labels, before proceeding to the training steps as described in the previous sections.
+
 %The procedure is quite straight-forward. While part of the team worked on
@@
 
-Before any learning happens, we begin by partitioning the dataset in two subsets: training and test.
-This split is achieved by first loading the entire dataset in memory and assigning the first 80\% examples to the validation set and the remaining 20\% to the test set.
-Doing so, we increase our confidence in the resulting accuracy.
-In preliminary experiments we observed that the majority of the models were highly overfitting the training set.
-In order to find better hyperparameters, we thus further partitioned the training set into a development and a validation set.
-(again an 80-20 split) Once the recall-variance trade-off reached a satisfactory level on the development and validation set, we train all models using the same hyperparameters on the entire (identical) training set, and evaluate them on the test set.
-
-The training for evaluation is performed as follows. We begin by training a single encoder and the decoder on a single modality.
-(eg, the content of the articles) We measure the obtained accuracy on the test set and serialize the model's parameters on disk.
-In the second step, we recreate the previously trained encoder and decoder, and initialize them with their respective serialized parameters.
-We also instantiate a new encoder architecturally identical to the first one but with untrained parameters.
-Finally, we load both the previous and the new modality from the dataset and their corresponding labels, before proceeding to the training steps as described in the previous sections.
-
 \section{Results}\label{results}
 
-\subsection{Single LSTM network}
+\subsection{Baseline System}
 

### 2016-04-29 paper/draft.tex
Fixed some typos and minor modifications to content

@@
 In this short paper, we propose a Modular Deep Encoder-Decoder network (MDED) for text classification.
-The basic idea behind MDED is to extend a pre-trained model, which consists of a set of deep encoder-decoders, with an additional source of data by adding a new encoder to the network.
+The basic idea behind MDED is to extend a pre-trained model, which consists of a set of deep encoder-decoders, with an additional source of data modality by adding a new encoder to the network.
 MDED has been applied to text classification on SaudiNewsNet.
@@
 
-In the past decade, deep learning has been successfully applied to natural language processing (NLP).
-It has been shown that end-to-end trained deep learning algorithms can outperform traditional algorithms on various NLP tasks.
-
-However, the training process of deep learning algorithms is usually very time-consuming.
-And it is inefficient to update a model and re-train it from scratch everytime there is a new data source coming.
+In the past decade, deep learning has gained a lot of momentum in various fields.
+It has been successfully applied to natural language processing (NLP).
+End-to-end trained deep learning algorithms have been proven to outperform traditional algorithms on various NLP tasks.
+The success of deep learning is accounted for trading off computationally complexity for performance.
+The high complexity demand for training deep learning algorithms is inefficient especially when there is new complementary data modality to be used to update a model and re-train it from scratch every time.
 To alleviate this problem, a novel Modular Deep Encoder-Decoder network (MDED) is proposed in this paper.
-The basic idea behind MDED is to extend a pre-trained model, which consists of a set of deep encoder-decoders, with an additional source of data by adding a new encoder to the network.
+The basic idea behind MDED is to extend a pre-trained model, which consists of a set of deep encoder-decoders, with an additional source of data modality by adding a new encoder to the network.
 
@@
 both use encoders on a sequence of data to generate a
-\emph{thought-vector} which will then be decoded in the desired terget
+\emph{thought-vector} which will then be decoded in the desired target
 sequence. In some sense, our proposal adds the transfer learning
@@
 images to their captions with embeddings.
+
+In this paper, we evaluate the effectiveness of idea by applying the concept towards a simple NLP classification task.
+We adopt an Arabic newspaper article database to classify into different journals based on the article content, author and title.
 
@@
 
-In oder to further improve the classification performance, new sources of training data are added to the base single LSTM network.
+In order to further improve the classification performance, new sources of training data are added to the base single LSTM network.
 For each single LSTM network, two other data source are added to it, respectively.
@@
 \hline
-Training acc   &                   &                  &                &                           &                           & \\
-Tesging acc   &                   &                  &                &                           &                           & \\
+Training accuracy   &                   &                  &                &                           &                           & \\
+Testing accuracy   &                   &                  &                &                           &                           & \\
 

### 2016-04-29 paper/draft.tex
Added Tools; Labor Division; Baseline Results;Hyperparameter tuning

@@
 The basic idea behind MDED is to extend a pre-trained model, which consists of a set of deep encoder-decoders, with an additional source of data modality by adding a new encoder to the network.
-MDED has been applied to text classification on SaudiNewsNet.
+MDED has been applied to text classification on Saudi Newspapers Arabic Corpus (SaudiNewsNet).
 A modular Long Short Term Memory (LSTM) network is built.
@@
 In this paper, we evaluate the effectiveness of idea by applying the concept towards a simple NLP classification task.
-We adopt an Arabic newspaper article database to classify into different journals based on the article content, author and title.
+We adopt Saudi Newspapers Arabic Corpus \cite{hagrima2015} to classify text into different journals based on the article content, author and title.
 
@@
 \subsection{Materials}
-We used the freely available dataset from
-\url{https://github.com/ParallelMazen/SaudiNewsNet} The dataset contains
-a total of 31,030 Arabic newspaper articles, with a total number of 8,758,976 words.
+\subsubsection{Corpora}
+We use the freely available Saudi Newspapers Arabic Corpus \cite{hagrima2015}. The dataset contains a total of 31,030 Arabic newspaper articles, with a total number of 8,758,976 words.
 
@@
 \end{figure}
+
+\subsubsection{Tools}
+For training the neural networks, Neon toolkit was employed \cite{Neon}.
+Neon is Nervana's python based deep-learning library.
+The toolkit was chosen because of its flexibility of distributed training on both CPU and GPU and its good support for neural network components.
 
@@
 
+\subsubsection{Hyper-parameter Tuning}
+Using the development set, the hyper-parameters were fine-tuned for better performance.
+The tuning of sentence length cut-off for training the embedding layer was found to be critical especially when training on the content of articles.
+Setting lower sentence length resulted in over-training of the system.
+The distribution of the sentence lengths were plotted as shown in Figure~\ref{fig:sent_dist}.
+Looking at the distribution, we found the value of 2048 to be optimal.
+Different values for learning rate, hidden-layer dimensionality and non-linearity were experimented.
 %The procedure is quite straight-forward. While part of the team worked on
@@
 
-Training accuracy &  &  &  \\
+Training accuracy &  & 83.5207\% & 88.8635\% \\
 
-Testing accuracy & & & \\
+Testing accuracy & & 79.7421 \% & 58.7276\% \\
 
@@
 
+\newpage
+\section{Labor Division}
+\begin{itemize}
+\item
+  \textbf{Cheng:} \textbf{Coding} - Data retrieval, unzipping, reading, unicode decoding; \textbf{Report Writing} - Corpora, Evaluation.
+\item
+  \textbf{Quiangui:} Hyper-parameter tuning; \textbf{Report Writing} - Results, Abstract, Introduction.
+\item
+  \textbf{Prashanth:} \textbf{Coding} - Data pre-processing, Data partitioning,  Feature representation for embedding layer, Baseline system; \textbf{Report Writing} - Data pre-processing and features, Embedding Layer, Baseline System, Hyper-parameter tuning.
+\item
+  \textbf{Sebastian:} \textbf{Coding} - Neural Network training, Makefiles; \textbf{Report Writing} - Abstract, Introduction, Proposed System, Discussion.
+\end{itemize}
+\section{Word Count}
 %\end{multicols}

### 2016-04-29 paper/draft.tex
Filled evaluation

@@
 The evaluation procedure for all experiments is based on the classification accuracy of each statistical model on a held-out validation set.
+Each time we use the newly built model to generate a result, and use the result from jointly trained model to compare.
+This held-out validation scheme has a better reprensentation of the negative or positive contribution the new model has, compared to just using the joint model's accuracy.
+We provide accuracy in the results.
+However, the accuracy is not enough.
+More meeaningful F1-score or AUC metrics will be provided during the future work.
 

### 2016-04-29 paper/draft.tex
added an arabic example
Removed title figure; Modified evaluation section; Added Discussion and future work; Added Word count;

--- 2016-04-29 paper/draft.tex
@@
 
+% This picture is not relevant to us
+%\begin{figure}[h!]
+%\centering
+%\includegraphics[width=\textwidth]{figures/title_example.png}
+%\caption{An example of an article title}
+%\end{figure}
+
 The dataset is partitioned into training, development and testing subsets.
@@
 \subsection{Evaluation}
-The evaluation procedure for all experiments is based on the classification accuracy of each statistical model on a held-out validation set.
+The evaluation procedure for all experiments is based on the classification accuracy of each statistical model on a held-out test data.
+Meanwhile, we identify that the accuracy is not an ideal evaluation criteria considering the skewed nature of class distribution.
+To get a more meaningful representation of the performance F1-score or AUC metrics will be provided in the future work.
+However we stress the validity of the accuracies provided in the results section by comparing it to the random baseline.
+Taking into account the multi-class (14 class problem) nature of the classification and the prior for each class, we would like to point out that the average accuracy or chance accuracy of the data is 9.68\% which forms the random baseline of the problem under investigation.
 
@@
 \section{Discussion}\label{discussion}
+The results of the baseline system for each modality by themselves show significant improvement over the random baseline.
+We asses that the author modality to be more informative for classification as expected due to low overlap of author names across journals.
+
+In future, more informative evaluation metrics in terms of F1-score and AUC will be provided for better reflection of performance of each system.
+We plan to also analyze the per class performance.
+We expect classes with less samples to be less accurate during classification because of data sparsity, which could be solved by discarding the classes with low sample counts thereby increasing the overall accuracy of the system.
+
+In future, we would like to apply the concept to other databases and pose the concept to solve inter-database learning.
+We could also prove the concept in other areas like speech, image and other signal processing domains.
 
@@
 \item
-  \textbf{Prashanth:} \textbf{Coding} - Data pre-processing, Data partitioning,  Feature representation for embedding layer, Baseline system; \textbf{Report Writing} - Data pre-processing and features, Embedding Layer, Baseline System, Hyper-parameter tuning.
+  \textbf{Prashanth:} \textbf{Coding} - Data pre-processing, Data partitioning,  Feature representation for embedding layer, Baseline system; \textbf{Report Writing} - Data pre-processing and features, Embedding Layer, Baseline System, Hyper-parameter tuning, Evaluation, Discussion.
 \item
@@
 \section{Word Count}
+\begin{itemize}
+\item
+109 Abstract
+\item
+392 Introduction
+\item
+254 Materials
+\item
+593 Procedure
+\item
+126 Evaluation
+\item
+60 Results: Baseline System
+\item
+92 Results: Modular LSTM network
+\item
+146 Discussion
+\item
+1772 Total
+\end{itemize}
 %\end{multicols}

### 2016-04-30 paper/draft.tex
update draft
update draft. results section added and minor modifications made

@@
 \usepackage{amsfonts}
+\usepackage{subcaption}
 \input{\string./core}
@@
 	\url{arnolds@usc.edu}\Mark{1} & \url{pgurunat@usc.edu}\Mark{2} & \url{chengqu@usc.edu}\Mark{3} & \url{qianguih@usc.edu}\Mark{4} \tabularnewline
-	9013085897 & 2251924199 & 9532576000 & 2385279985
+	9013085897 & 2251924199 & 2385279985 & 9532576000
 	\end{tabular}\par
@@
 Experimental results show that our algorithm can efficiently combine new source of data and pre-trained model.
-(show some summaries of experimental results here)
+The training process can converge into a local optimum in very few epochs when a new data source is added.
+With a good initial encoder-decoder, the modular LSTM networks can improve classification accuracy by up to 0.51\% when a new data source is added.
 
@@
 Different values for learning rate, hidden-layer dimensionality and non-linearity were experimented.
+Through a series of experiments, we found the optimal setting for initial learning rate is 0.01, optimal hidden-layer dimensionality is 128, and tangent function is the optimal activation function in hidden layers.
+
 %The procedure is quite straight-forward. While part of the team worked on
@@
 First, three single LSTM networks are trained for text classification, where title, author and content values are used for training data, respectively.
-The classification performance of them are reported in Table.\ref{single_lstm_acc}.
-From Table.\ref{single_lstm_acc} we can see that xxx model has the best classification performance among these three models.
+The hyper-parameter setting is same as introduced in above section.
+The batchsize is 32 and training ends after 10 epochs.
+
+The classification performance of these models are reported in Table.\ref{single_lstm_acc}.
+From Table.\ref{single_lstm_acc} we can see that author model has the best classification performance (73.89\%)  among these three models.
+And title model has the worst performance (21.23\%) although its training accuracy achieves 92.93\%, which means training using only the title of articles will result in serious overfitting.
 
@@
 \hline
-Training data & Title & Author & Content\\
+Training data & Title & Content & Author\\
 \hline
 
-Training accuracy &  & 83.5207\% & 88.8635\% \\
+Training accuracy (\%) & 92.93  & 96.31 & 85.41\\
 
-Testing accuracy & & 79.7421 \% & 58.7276\% \\
+Testing accuracy (\%) & 21.23  & 43.68 & \textbf{73.89} \\
 
@@
 \begin{center}
-%\includegraphics[width=2.8in]{path_sample.eps}
+\includegraphics[width=5in]{figures/loss_training_single.png}
 \end{center}
@@
 In order to further improve the classification performance, new sources of training data are added to the base single LSTM network.
-For each single LSTM network, two other data source are added to it, respectively.
+For each single LSTM network, one new data source is added to it, respectively.
 For example, for content LSTM network, author of the articles and title of the articles are added to it as an additional source of training data.
 Technically, a new encoder is added to the original LSTM network.
+The training parameters are same as above.
 Performance of these modular LSTM networks are reported in Table.\ref{modular_lstm_acc}.
+
+Experimental results show that our modular LSTM networks can effectively exploit new data source in most of the cases.
+For the author model, which is trained using only author of articles, the classification accuracy has been improved by 0.57\%.
+One interesting finding is that after adding a new data source to content model, the classification is decreased by 0.34\% and 1.31\%.
+We can also find that the content-author model \footnote{author is the based data source and content is the added data source} has a much better performance than author-content model.
+That's because the single author model has a better performance than the single content model, which demonstrates that a good initial model is very crucial in modular LSTM networks.
 
@@
 \hline
-Training accuracy   &                   &                  &                &                           &                           & \\
-Testing accuracy   &                   &                  &                &                           &                           & \\
+Training accuracy (\%)   & 95.59  &   95.51    &   97.12   &   97.13    &  86.48  & 85.79\\
+Testing accuracy (\%)   &  21.69  &     21.64   &   42.37  &    43.34   &  \textbf{74.46}    & 74.04\\
+\hline
+Improvement (\%) &           0.46 &     0.41     &      -1.31    &    -0.34  &   \textbf{0.57}   & 0.15 \\
 
@@
 
-Moreover, the training behavior of them are presented in Fig.\ref{training_loss_modular}.
+\begin{figure}[!t]
+\begin{subfigure}{1\textwidth}
+  \centering
+   \includegraphics[width=4in]{figures/loss_training_title_modular.png}
+   \caption{}
+   \label{modular_loss_title}
+\end{subfigure}
 
-\begin{figure}[!t]
-\begin{center}
-%\includegraphics[width=2.8in]{path_sample.eps}
-\end{center}
-\caption{Training loss and testing loss of modular LSTM networks.}
-\label{training_loss_modular}
+\begin{subfigure}{1\textwidth}
+  \centering
+   \includegraphics[width=4in]{figures/loss_training_content_modular.png}
+   \caption{}
+   \label{modular_loss_title}
+\end{subfigure}
+
+\begin{subfigure}{1\textwidth}
+  \centering
+   \includegraphics[width=4in]{figures/loss_training_author_modular.png}
+   \caption{}
+   \label{modular_loss_title}
+\end{subfigure}
+
+\caption{Training loss and testing loss of modular LSTM networks: (a) title model based modular LSTM; (b) content model based modular LSTM; (c) author based modular LSTM.
+In the legends content-title author-title, and etc., the previous one denotes base data source and latter one denotes added data source.}
+\label{modular_loss}
 \end{figure}
+
+Moreover, the training behavior of them are presented in Fig.\ref{modular_loss}.
+In Fig.\ref{modular_loss}, the  training loss of initial single LSTM and modular LSTm networks are compared with each other.
+From Fig.\ref{modular_loss} we can see that, in all three cases, after a new data source is added, the training loss can converge to a local optimal very fast and the loss values accordingly decrease rapidly.
+Once a new data source is added, the whole training process can finish in less than 1,000 iterations (near 2 epochs).
+This demonstrates the efficiency of our MDED network.
 
@@
 \item
-  \textbf{Quiangui:} Hyper-parameter tuning; \textbf{Report Writing} - Results, Abstract, Introduction.
+  \textbf{Quiangui:} \textbf{Coding} - Core model and augmented model training, Data partitioning, Word2vec model, Training log parsing, Hyper-parameter tuning, Model training, Makefiles.
+\textbf{Report Writing} - Abstract, Introduction, Hyper-parameter tuning, Results.
 \item

### 2016-04-30 experiment/networks.py
update training scripts
update training scripts

@@ -52,7 +52,7 @@ def get_core_net(embedding_size=128, vocab_size=20000, nout=10, dropout_rate = 0
     if activation_function == 4:
         af = Normalizer()
 
-
+    
     embedding_dim = embedding_size
     uni = Uniform(low=-0.1/embedding_dim, high=0.1/embedding_dim)
     glorot = GlorotUniform()
@@ -64,7 +64,6 @@ def get_core_net(embedding_size=128, vocab_size=20000, nout=10, dropout_rate = 0
     ]
 
     dec = [
-        Dropout(keep=0.25),
         Dropout(keep=dropout_rate),
         Affine(nout, glorot, bias=glorot, activation=Softmax())
     ]
@@ -73,7 +72,7 @@ def get_core_net(embedding_size=128, vocab_size=20000, nout=10, dropout_rate = 0
     return (enc, dec), cost, opt
 
 
-def load_core(file_prefix, embedding_size=128):
+def load_core(file_prefix,embedding_size=128):
     enc = Model(file_prefix + '_encoder.neon').layers.layers
     dec = Model(file_prefix + '_decoder.neon').layers.layers
     return enc, dec
@@ -102,3 +101,4 @@ def get_title_augmentor(vocab_size=20000, embedding_size=128, path=None):
     ]
     cost, opt = get_cost_opt()
     return aug, cost, opt
+

### 2016-04-30 experiment/train.py

@@ -99,10 +99,8 @@ ntrain, nvalid, nclass, vocab_size = data.attrs['ntrain'], data.attrs['nvalid'],
 # X_valid, y_valid = get_paddedXY(X, y, vocab_size=vocab_size, sentence_length=sentence_length)
 # valid_set = ArrayIterator(X_valid, y_valid, nclass=nclass)
 
-#train_set, valid_set, nout = get_saudinet_data(args)
-(X_train, y_train), (X_test, y_test), nout, vocab_size = get_saudinet_data(args, modality='content')
-train_set = ArrayIterator(X_train, y_train, nout)
-test_set = ArrayIterator(X_test, y_test, nout)
+train_set, valid_set, nout = get_saudinet_data(args)
+
 
 # initialization
 init_glorot = GlorotUniform()

### 2016-04-30 experiment/train_augmented.py

@@ -45,24 +45,35 @@ class MultiModalModel(Model):
 if __name__ == '__main__':
     # parse the command line arguments
     parser = NeonArgparser(__doc__)
+    parser.add_argument("-nds","--new_data_source", help = "choose the data source used for classification. options: content, title, author, author-content, author-title, content-title. defaul: title")
+    parser.add_argument("-im","--initial_model", help = "choose the initial encoder-decoder model. options: content, title, author. default: content")
+    
+
     args = parser.parse_args(gen_be=False)
 
     # hyperparameters from the reference
     args.batch_size = 32
     args.backend = 'gpu'
-    modal1 = 'content'
-    modal2 = 'authors'
+   
 
+    if not args.new_data_source:
+      args.new_data_source = 'title'
+
+    if not args.initial_model:
+      args.initial_model = 'content'
+     
+
+ 
+    print ' '
+    print "new source used for classification is: ", args.new_data_source
+    print "initial model is trained on: ", args.initial_model
+    print ' '
+    
+    
     # Setup backend
     be = gen_backend(**extract_valid_args(args, gen_backend))
 
     # Load the dataset
-<<<<<<< Updated upstream
-    (X_train_content, y_train_content), (X_test_content, y_test_content), nout, vocab_size = get_saudinet_data(args, modality=modal1)
-    (X_train_title, y_train_title), (X_test_title, y_test_title), nout, vocab_size = get_saudinet_data(args, modality=modal2)
-    train_set = ArrayIterator([X_train_content, X_train_title], y_train_content, nout)
-    test_set = ArrayIterator([X_test_content, X_test_title], y_test_content, nout)
-=======
     (X_train_content, y_train_content), (X_test_content, y_test_content), nout, vocab_size = get_saudinet_data(args, modality='content')
     (X_train_title, y_train_title), (X_test_title, y_test_title), nout, vocab_size = get_saudinet_data(args, modality='title')
     (X_train_authors, y_train_authors), (X_test_authors, y_test_authors), nout, vocab_size = get_saudinet_data(args, modality='author')
@@ -84,10 +95,10 @@ if __name__ == '__main__':
 
     X_train['author-content-title'], X_test['author-content-title'] = [X_train_authors, X_train_content,X_train_title], [X_test_authors, X_test_content,X_test_title]
 
[…]

### 2016-04-30 experiment/train_core.py

@@ -23,23 +23,44 @@ import argparse
 if __name__ == '__main__':
     #parse parameter settings from command line
     parser = NeonArgparser(__doc__)
-    # parser.add_argument("data_source", help="choose the data source to train initial encoder-decoder. defaul is content")
-    # parser.add_argument("-lr", "--learning_rate", type = float, help="set the learning rate. defaul 0.01")
-    # parser.add_argument("-es", "--embedding_size", type = int, help = "set the embedding size. default 128")
-    # parser.add_argument("-dr", "--dropout_rate", type = float, help = "set the dropout rate. default 0.5")
-    # parser.add_argument("-af", "--activation_function", type = int, help = "set the activation default: Tanh; 1: Tanh, 2: ReLU, 3: Sigmoid, 4: Normalizer")
-
+    parser.add_argument("-ds","--data_source", help="choose the data source to train initial encoder-decoder. defaul is content")
+    parser.add_argument("-lr", "--learning_rate", type = float, help="set the learning rate. defaul 0.01")
+    parser.add_argument("-es", "--embedding_size", type = int, help = "set the embedding size. default 128")
+    parser.add_argument("-dr", "--dropout_rate", type = float, help = "set the dropout rate. default 0.5")
+    parser.add_argument("-af", "--activation_function", type = int, help = "set the activation default: Tanh; 1: Tanh, 2: ReLU, 3: Sigmoid, 4: Normalizer")
+    
     args = parser.parse_args(gen_be=False)
 
     # hyperparameters from the reference
-    args.batch_size = 128
+    #args.batch_size = 128
+    args.batch_size = 32 
     args.backend = 'gpu'
+   
 
-    modality = 'content'
-    learning_rate = 0.01
-    embedding_size = 128
-    dropout_rate = 0.5
-    activation_function = 1
+    if args.data_source:
+        data_source = args.data_source
+    else:
+        args.data_source = 'content' 
+    
+    if args.learning_rate:
+        learning_rate = args.learning_rate
+    else:
+        learning_rate = 0.01
+    
+    if args.embedding_size:
+        embedding_size = args.embedding_size
+    else:
+        embedding_size = 128
+    
+    if args.dropout_rate:
+        dropout_rate = args.dropout_rate
+    else:
+        dropout_rate = 0.5
+    
+    if args.activation_function:
+        activation_function = args.activation_function
+    else:
+        activation_function = 1
 
[…]

### 2016-04-30 experiment/data.py
update data.py
update preprocess_data_train module in data.py to generate same set of
training and testing data for different models. Using random seed may
result in different training and testing data divisions.

@@ -184,7 +184,6 @@ def preprocess_data_train(data, query, path='.', filepath='labeledTrainData.tsv'
                 data_ = clean_string_unicode(data[i][key])
                 data_words = data_.strip().split()
                 num_words = len(data_words)
-                split = int(np.random.rand() < train_ratio)
 
                 # create record
                 if query == key:

### 2016-04-30 experiment/data.py
update data.py
update preprocess_data_train module in data.py to generate same set of
training and testing data for different models. Using random seed may
result in different training and testing data divisions.

@@ -18,6 +18,7 @@ from neon.data.text_preprocessing import get_paddedXY
 from neon.data import ArrayIterator
 from neon.data.dataloaders import load_imdb
 from neon.data.text_preprocessing import pad_data
+
 import matplotlib
 matplotlib.use('Agg')
 import matplotlib.pyplot as plt
@@ -25,6 +26,8 @@ import matplotlib.patches as mpatches
 
 SENTENCE_LENGTH = 1024
 blue_patch = mpatches.Patch(color="blue", label="Dataset")
+
+SENTENCE_LENGTH = 128
 
 
 def get_saudinet_data(args, modality='content'):
@@ -45,6 +48,7 @@ def get_saudinet_data(args, modality='content'):
     y = [xy[0] for xy in Xy]
     X_train, y_train = get_paddedXY(X, y, vocab_size=vocab_size, sentence_length=SENTENCE_LENGTH)
     # train_set = ArrayIterator(X_train, y_train, nclass=nclass)
+    
     journals, counts = np.unique(y, return_counts=True)
     print 'Train set class distribution - ', journals, counts
     plt.bar(journals, counts, 1/1.5, color="green")
@@ -58,12 +62,14 @@ def get_saudinet_data(args, modality='content'):
     y = [xy[0] for xy in Xy]
     X_valid, y_valid = get_paddedXY(X, y, vocab_size=vocab_size, sentence_length=SENTENCE_LENGTH)
     # valid_set = ArrayIterator(X_valid, y_valid, nclass=nclass)
+    
     journals, counts = np.unique(y, return_counts=True)
     print 'Validation set class distribution - ', journals, counts
     plt.bar(journals, counts, 1/1.5, color="red")
     red_patch = mpatches.Patch(color="red", label="Test Set")
     plt.legend(handles=[blue_patch,green_patch,red_patch])
     plt.savefig('./test_class_distribution.png')
+    
 
     return (X_train, y_train), (X_valid, y_valid), nclass, vocab_size
 
@@ -137,8 +143,11 @@ def clean_string_unicode(string):
     # string = regex.sub(ur"\s{2,}", " ", string)
     return string.strip()
 
+
 def preprocess_data_train(data, query, path='.', filepath='labeledTrainData.tsv', vocab_file=None, vocab=None, train_ratio=0.8):
+
     np.random.seed(1234)
+
     fname_h5 = filepath + '.h5'
     if vocab_file is None:
         fname_vocab = filepath + '.vocab'
[…]

### 2016-04-30 experiment/parse_loss.py
create parse_loss.py
create parse_loss.py to parse loss values from log files

@@ -1,0 +1,33 @@
+
+"""
+parse the loss function values in log file into a txt file for visualization
+
+Example usage:
+    python parse_loss.py title_author.pbs.o14844248 title_author_loss.txt    
+
+"""
+
+import argparse
+import numpy as np
+
+parser = argparse.ArgumentParser()
+parser.add_argument("input",help="input log file")
+parser.add_argument("output",help="output file")
+
+args = parser.parse_args()
+
+
+f = open(args.input)
+content = f.read()
+f.close()
+
+content = content.split()
+
+with open(args.output,'w') as f:
+    for i in range(len(content)):
+        if content[i] == 'cost,':
+            f.write(content[i-1])
+            f.write('\n')
+
+
+

### 2016-04-30 paper/draft.tex
Added more text to draft, resized figures.

@@
 \title{Modular Deep Encoder-Decoders}
-\author{Sebastian Arnold\Mark{1}, Prashanth Gurunath Shivakumar\Mark{2}, Cheng Qu\Mark{3}\\ and Qiangui Huang\Mark{4}}
+\author{Sebastien Arnold\Mark{1}, Prashanth Gurunath Shivakumar\Mark{2}, Cheng Qu\Mark{3}\\ and Qiangui Huang\Mark{4}}
 %\affil[1]{Department of Computer Science, University of Southern California, Los Angeles, CA \authorcr Email: {\tt \{arnolds, chengqu, qianguih\}@usc.edu}\vspace{1.5ex}}
@@
 \centering
-\includegraphics{figures/multimodal.png}
+\includegraphics[width=0.5\textwidth]{figures/multimodal.png}
 \caption{Multi-modal Transfer Learning}
@@
 and have been known to highly outperform other statistical techniques on
-natural language tasks. Learning embeddings has been previously done by
+natural language tasks. Learning embeddings has been previously done by Zhuang \& al in 
 \cite{zhuang2015supervised}, although our proposed contribution is
-slightly different. \cite{zhuang2015supervised} used deep autoencoders to
+slightly different. They used deep autoencoders to
 obtain a better initialization of the parameters of their model. Our
-approach instead is much closer in spirit to the work of Sutskever
-\cite{sutskever2014sequence} and Vinyals \cite{vinyals2015grammar}. They
+approach instead is much closer in spirit to the work of Sutskever \& al
+\cite{sutskever2014sequence} and Vinyals \& al \cite{vinyals2015grammar}. They
 both use encoders on a sequence of data to generate a
@@
 \centering
-\includegraphics[width=\textwidth]{figures/article-newspaper_distribution.png}
+\includegraphics[width=0.65\textwidth]{figures/article-newspaper_distribution.png}
 \caption{Figure shows article-newspaper distribution}
@@
 \centering
-\includegraphics[width=\textwidth]{figures/test_class_distribution.png}
+\includegraphics[width=0.65\textwidth]{figures/test_class_distribution.png}
 \caption{Distribution of data for training and testing}\label{fig:dist}
@@
 \centering
-\includegraphics[width=\textwidth,height=6cm]{figures/sentence_length.png}
+\includegraphics[width=0.65\textwidth,height=6cm]{figures/sentence_length.png}
 \caption{Distribution of data for training and testing}\label{fig:sent_dist}
@@
 \subsubsection{Tools}
-For training the neural networks, Neon toolkit was employed \cite{Neon}.
+For training the neural networks, the neon toolkit was employed \cite{Neon}.
 Neon is Nervana's python based deep-learning library.
-The toolkit was chosen because of its flexibility of distributed training on both CPU and GPU and its good support for neural network components.
+The toolkit was chosen because of its flexibility of training on both CPU and GPU, its good support for neural network components, and it's state-of-the-art performance on GPU.
+In addition, one of the team members is a core contrubtor to the framework.
 
@@
 
-We tried two approaches when building the vector embedding from multiple modalities.
-The first one was to vertically stack the different embeddings from the different encoders and learn the actual embedding from a linear combination from this higher dimensional vector.
-This led to poor results and we instead decided to experiment with both the summing over every embedding, as well as taking their mean in each dimension.
-
 %\subsubsection{Discriminative Model}
@@
 systems.
-The baseline system is a recurrent neural network with one hidden Long Short Term Memory (LSTM) layer succeeding the embedding layer.
+The encoder of the baseline system is a recurrent neural network with one hidden Long Short Term Memory (LSTM) layer succeeding the embedding layer.
 The dimension of both the embedding layer and the LSTM was fixed to 128.
-The output layer is a softmax layer with 14 outputs, one per class.
-The model minimize a cross-entropy loss using adaptive gradient descent.
-\cite{duchi2011adaptive}
+The decoder is a softmax layer with 14 outputs, one per class.
+The model minimize a cross-entropy loss using adaptive gradient descent \cite{duchi2011adaptive}.
 
 \subsubsection{Proposed System}
-The training for evaluation is performed as follows. We begin by training a single encoder and the decoder on a single modality.
-(eg, the content of the articles) We measure the obtained accuracy on the test set and serialize the model's parameters on disk.
-In the second step, we recreate the previously trained encoder and decoder, and initialize them with their respective serialized parameters.
-We also instantiate a new encoder architecturally identical to the first one but with untrained parameters.
-Finally, we load both the previous and the new modality from the dataset and their corresponding labels, before proceeding to the training steps as described in the previous sections.
+Once the baseline encoder and decoder have been trained on a single modality, we serialize their parameters on disk.
+We then proceed to the augmentation of our model by adding a new encoder.
+We first jointly load both modalities from the dataset - in our case the authors and the content of the articles - as well as their targets.
+We then instanciate two encoders and one decoder with random initialization.
+The parameters of the decoder and of one of the encoder are set from the serialized values obtained from the baseline.
+We then proceed by training our augmented model on both modalities.
+To ensure that the parameters of the initial encoder are not changed, we manually set the scaling factor of the gradients to zero.
+This results in the backpropagated errors - the partial derivatives of the errors with respect to the inputs - to be zero and the adaptive gradient descent step to have no effect.
+
+Both of the encoders use an identical structure independently of the modality they are trained on. This model architecture is identical to the one described in the baseline system subsection.
+
+We tried two approaches when building the vector embedding from multiple modalities.
+The first one was to vertically stack the different embeddings from the different encoders and learn the actual embedding as a linear combination from this higher dimensional vector.
+This led to poor results and we instead decided to experiment with both the summing over every embedding, as well as taking their mean in each dimension.
+Both approaches resulted in fairly similar results, however and we decided to use the mean of the embeddings in our experiments.
+The intuition behind this decision is grounded in the observation that taking the mean of several embeddings will have a less drastical effect on the decoder, thus stabilizing the learning in early stages of the transfer training.
 
@@
 
+\begin{figure}[!t]
+\begin{subfigure}{1\textwidth}
+  \centering
+   \includegraphics[width=4in]{figures/loss_training_title_modular.png}
+   \caption{}
+   \label{modular_loss_title}
+\end{subfigure}
+
+\begin{subfigure}{1\textwidth}
+  \centering
+   \includegraphics[width=4in]{figures/loss_training_content_modular.png}
+   \caption{}
+   \label{modular_loss_title}
+\end{subfigure}
+
+\begin{subfigure}{1\textwidth}
+  \centering
+   \includegraphics[width=4in]{figures/loss_training_author_modular.png}
+   \caption{}
+   \label{modular_loss_title}
+\end{subfigure}
+
+\caption{Training loss and testing loss of modular LSTM networks: (a) title model based modular LSTM; (b) content model based modular LSTM; (c) author based modular LSTM.
+In the legends content-title author-title, and etc., the previous one denotes base data source and latter one denotes added data source.}
+\label{modular_loss}
+\end{figure}
+
 \subsection{Modular LSTM network}
@@
 
-\begin{figure}[!t]
-\begin{subfigure}{1\textwidth}
-  \centering
-   \includegraphics[width=4in]{figures/loss_training_title_modular.png}
-   \caption{}
-   \label{modular_loss_title}
-\end{subfigure}
-
-\begin{subfigure}{1\textwidth}
-  \centering
-   \includegraphics[width=4in]{figures/loss_training_content_modular.png}
-   \caption{}
-   \label{modular_loss_title}
-\end{subfigure}
-
-\begin{subfigure}{1\textwidth}
-  \centering
-   \includegraphics[width=4in]{figures/loss_training_author_modular.png}
-   \caption{}
-   \label{modular_loss_title}
-\end{subfigure}
-
-\caption{Training loss and testing loss of modular LSTM networks: (a) title model based modular LSTM; (b) content model based modular LSTM; (c) author based modular LSTM.
-In the legends content-title author-title, and etc., the previous one denotes base data source and latter one denotes added data source.}
-\label{modular_loss}
-\end{figure}
-
 Moreover, the training behavior of them are presented in Fig.\ref{modular_loss}.
-In Fig.\ref{modular_loss}, the  training loss of initial single LSTM and modular LSTm networks are compared with each other.
-From Fig.\ref{modular_loss} we can see that, in all three cases, after a new data source is added, the training loss can converge to a local optimal very fast and the loss values accordingly decrease rapidly.
+The  training loss of initial single LSTM and modular LSTM networks are compared with each other.
+From Fig.\ref{modular_loss} we can see that, in all three cases, after a new data source is added the training loss can converge to a local optimal very fast and the loss values accordingly decrease rapidly.
 Once a new data source is added, the whole training process can finish in less than 1,000 iterations (near 2 epochs).
 This demonstrates the efficiency of our MDED network.
-
-%Needs results for:
-
-%1. single model on authors
-%2. single model on content
-%3. single model on titles
-%4. multimodal on authors-content
-%5. multimodal on title-content
-%6. ? multimodal author-titles ?
-
-%TODO: Say if we ended up using RecurrentSum or RecurrentMean for the embedding. (see embedding layer section)
 
@@
 We asses that the author modality to be more informative for classification as expected due to low overlap of author names across journals.
+In addition to the improved accuracy and fast convergence of the system, further improvement in the computational time could be gained by avoiding the optimization step of the trained encoders.
+In fact, in this paper we only cancel the effect of adaptive gradient descent on the baseline encoder by setting the gradients to zero, but the computations are still carried out.
+This improvement could be included in frameworks that take advantage of MDEDs for transfer learning.
 
-In future, more informative evaluation metrics in terms of F1-score and AUC will be provided for better reflection of performance of each system.
+In future work, more informative evaluation metrics in terms of F1-score and AUC will be provided for better reflection of performance of each system.
 We plan to also analyze the per class performance.
@@
 
-In future, we would like to apply the concept to other databases and pose the concept to solve inter-database learning.
+In future work, we would like to apply the concept to other databases and pose the concept to solve inter-database learning.
 We could also prove the concept in other areas like speech, image and other signal processing domains.
@@
 \item
-  \textbf{Sebastian:} \textbf{Coding} - Neural Network training, Makefiles; \textbf{Report Writing} - Abstract, Introduction, Proposed System, Discussion.
+    \textbf{Sébastien:} \textbf{Coding} - Core and augmented model definition, experimental results; \textbf{Report Writing} - Proposal, Presentation, Abstract, Introduction, Proposed System, Discussion.
 \end{itemize}
@@
 \item
-593 Procedure
+757 Procedure
 \item
@@
 \item
-146 Discussion
+224 Discussion
 \item
-1772 Total
+2034 Total
 \end{itemize}
